---
title: "Ingest local league data and tracking"
output: html_document
---

## Purpose

This Rmd pulls authenticated SuperCoach league data, stores historical snapshots safely across reruns, rebuilds the latest known team state, preserves the verified cash-per-round logic, and emits checklist-oriented lookup tables using only confirmed production sources.

## Outputs

This script writes the following `.rds` files under the league-specific data folder:

- `ladder_history.rds`
- `fixtures_history.rds`
- `fixture_triggers.rds`
- `team_players_snapshots.rds`
- `team_players_latest.rds`
- `team_round_signatures.rds`
- `team_round_stats_history.rds`
- `actual_trade_history.rds`
- `inferred_changes.rds`
- `run_log.rds`
- `player_price_history_2026.rds`
- `players_cf_2026.rds`
- `player_id_lookup.rds`
- `player_price_history_sc.rds`
- `master_player_round_latest.rds`
- `opponent_behaviour_history.rds`
- `squad_round_enriched.rds`
- `game_rules_round_state.rds`
- `player_scoring_component_history.rds`
- `team_list_role_certainty.rds`
- `fixture_matchup_table.rds`
- `team_performance_context.rds`
- `cash_generation_model.rds`
- `league_ownership_movement.rds`
- `availability_risk_table.rds`
- `captaincy_vc_table.rds`
- `structure_health_table.rds`
- `scenario_refresh_table.rds`
- `long_horizon_planning_table.rds`
- `checklist_coverage_status.rds`

## 1. Setup

```{r}
suppressPackageStartupMessages({
  library(jsonlite)
  library(dplyr)
  library(tibble)
  library(purrr)
  library(tidyr)
  library(stringr)
  library(knitr)
})
```

## 2. Configuration

```{r}
league_id <- 21064L
season_rounds <- 1:27
base_url <- "https://www.supercoach.com.au/2026/api/nrl/classic/v1"
run_ts <- Sys.time()
season_year <- 2026L

if (!nzchar(Sys.getenv("SC_BEARER"))) {
  stop("SC_BEARER must be set in the environment before rendering this Rmd")
}

data_dir <- file.path("data", paste0("supercoach_league_", league_id))
dir.create(data_dir, recursive = TRUE, showWarnings = FALSE)

path_ladder_history <- file.path(data_dir, "ladder_history.rds")
path_fixtures_history <- file.path(data_dir, "fixtures_history.rds")
path_fixture_triggers <- file.path(data_dir, "fixture_triggers.rds")
path_team_players_snapshots <- file.path(data_dir, "team_players_snapshots.rds")
path_team_players_latest <- file.path(data_dir, "team_players_latest.rds")
path_team_round_signatures <- file.path(data_dir, "team_round_signatures.rds")
path_team_round_stats_history <- file.path(data_dir, "team_round_stats_history.rds")
path_actual_trade_history <- file.path(data_dir, "actual_trade_history.rds")
path_inferred_changes <- file.path(data_dir, "inferred_changes.rds")
path_run_log <- file.path(data_dir, "run_log.rds")
path_player_price_history_2026 <- file.path(data_dir, "player_price_history_2026.rds")
path_players_cf_2026 <- file.path(data_dir, "players_cf_2026.rds")
path_player_id_lookup <- file.path(data_dir, "player_id_lookup.rds")
path_player_price_history_sc <- file.path(data_dir, "player_price_history_sc.rds")
path_master_player_round_latest <- file.path(data_dir, "master_player_round_latest.rds")
path_opponent_behaviour_history <- file.path(data_dir, "opponent_behaviour_history.rds")
path_squad_round_enriched <- file.path(data_dir, "squad_round_enriched.rds")
path_game_rules_round_state <- file.path(data_dir, "game_rules_round_state.rds")
path_player_scoring_component_history <- file.path(data_dir, "player_scoring_component_history.rds")
path_team_list_role_certainty <- file.path(data_dir, "team_list_role_certainty.rds")
path_fixture_matchup_table <- file.path(data_dir, "fixture_matchup_table.rds")
path_team_performance_context <- file.path(data_dir, "team_performance_context.rds")
path_cash_generation_model <- file.path(data_dir, "cash_generation_model.rds")
path_league_ownership_movement <- file.path(data_dir, "league_ownership_movement.rds")
path_availability_risk_table <- file.path(data_dir, "availability_risk_table.rds")
path_captaincy_vc_table <- file.path(data_dir, "captaincy_vc_table.rds")
path_structure_health_table <- file.path(data_dir, "structure_health_table.rds")
path_scenario_refresh_table <- file.path(data_dir, "scenario_refresh_table.rds")
path_long_horizon_planning_table <- file.path(data_dir, "long_horizon_planning_table.rds")
path_checklist_coverage_status <- file.path(data_dir, "checklist_coverage_status.rds")
```

## 3. Helper functions

```{r}
`%||%` <- function(a, b) {
  if (is.null(a) || length(a) == 0) b else a
}

read_rds_if_exists <- function(path, default) {
  if (file.exists(path)) readRDS(path) else default
}

normalise_player_name <- function(x) {
  x %>%
    stringr::str_to_lower() %>%
    stringr::str_replace_all("\\*+", " ") %>%
    stringr::str_replace_all("[`´‘’']", "") %>%
    stringr::str_replace_all("[^a-z0-9, ]", " ") %>%
    stringr::str_squish() %>%
    stringr::str_replace_all(" ", "")
}

coalesce_chr <- function(x) {
  x <- as.character(x)
  x[is.na(x)] <- ""
  x
}

safe_chr <- function(x, default = NA_character_) {
  if (is.null(x) || length(x) == 0) return(default)
  as.character(x[[1]])
}

safe_int <- function(x, default = NA_integer_) {
  if (is.null(x) || length(x) == 0) return(default)
  suppressWarnings(as.integer(x[[1]]))
}

safe_dbl <- function(x, default = NA_real_) {
  if (is.null(x) || length(x) == 0) return(default)
  suppressWarnings(as.numeric(x[[1]]))
}

safe_lgl <- function(x, default = NA) {
  if (is.null(x) || length(x) == 0) return(default)
  as.logical(x[[1]])
}

list_to_chr <- function(x) {
  if (length(x) == 0) return(NA_character_)
  paste(as.character(unlist(x)), collapse = ", ")
}

build_url <- function(base, query = list()) {
  query <- query[!vapply(query, is.null, logical(1))]
  if (length(query) == 0) {
    return(base)
  }

  encoded <- purrr::imap_chr(
    query,
    ~ paste0(
      utils::URLencode(.y, reserved = TRUE),
      "=",
      utils::URLencode(as.character(.x), reserved = TRUE)
    )
  )

  paste0(base, "?", paste(encoded, collapse = "&"))
}

sc_headers <- function() {
  c(
    Accept = "application/json",
    Authorization = paste("Bearer", Sys.getenv("SC_BEARER")),
    Referer = paste0(
      "https://www.supercoach.com.au/nrl/classic/leagues(popup:leagues/",
      league_id,
      "/head-2-head)"
    ),
    Origin = "https://www.supercoach.com.au",
    "User-Agent" = "Mozilla/5.0"
  )
}

stats_headers <- function() {
  c("User-Agent" = "Mozilla/5.0")
}

http_get_text <- function(url, headers = character()) {
  con <- base::url(url, headers = headers)
  on.exit(try(close(con), silent = TRUE), add = TRUE)
  paste(readLines(con, warn = FALSE), collapse = "\n")
}

sc_get_json <- function(path, query = list()) {
  url <- build_url(paste0(base_url, path), query)
  txt <- http_get_text(url, sc_headers())
  jsonlite::fromJSON(txt, simplifyVector = FALSE)
}

stats_get_json <- function(url, query = list()) {
  full_url <- build_url(url, query)
  txt <- http_get_text(full_url, stats_headers())
  jsonlite::fromJSON(txt, simplifyVector = FALSE)
}

bind_rows_safe <- function(x) {
  if (is.null(x) || length(x) == 0) {
    tibble()
  } else {
    bind_rows(x)
  }
}

parallel_map <- function(x, f, mc.cores = max(1L, min(6L, parallel::detectCores() - 1L))) {
  if (length(x) <= 1 || .Platform$OS.type == "windows" || mc.cores <= 1) {
    return(lapply(x, f))
  }
  parallel::mclapply(x, f, mc.cores = mc.cores)
}

roll_mean_right <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) < k) return(out)
  for (i in seq.int(k, length(x))) {
    window <- x[(i - k + 1):i]
    if (all(!is.na(window))) {
      out[i] <- mean(window)
    }
  }
  out
}

roll_sd_right <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) < k) return(out)
  for (i in seq.int(k, length(x))) {
    window <- x[(i - k + 1):i]
    if (sum(!is.na(window)) >= 2) {
      out[i] <- stats::sd(window, na.rm = TRUE)
    }
  }
  out
}

roll_min_right <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) < k) return(out)
  for (i in seq.int(k, length(x))) {
    window <- x[(i - k + 1):i]
    if (all(!is.na(window))) {
      out[i] <- min(window)
    }
  }
  out
}

roll_max_right <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) < k) return(out)
  for (i in seq.int(k, length(x))) {
    window <- x[(i - k + 1):i]
    if (all(!is.na(window))) {
      out[i] <- max(window)
    }
  }
  out
}

build_roster_signature <- function(df) {
  if (nrow(df) == 0 || !"player_id" %in% names(df)) return(NA_character_)

  df %>%
    transmute(
      sig = paste(
        coalesce_chr(player_id),
        coalesce_chr(position),
        coalesce_chr(position_long),
        coalesce_chr(position_sort),
        coalesce_chr(picked),
        sep = "::"
      )
    ) %>%
    arrange(sig) %>%
    pull(sig) %>%
    paste(collapse = "|")
}

extract_roster_membership <- function(df) {
  if (nrow(df) == 0 || !"player_id" %in% names(df)) {
    return(tibble(player_id = integer()))
  }

  df %>%
    filter(!is.na(player_id)) %>%
    distinct(player_id) %>%
    arrange(player_id)
}

pair_inferred_trades <- function(players_out, players_in) {
  n_out <- length(players_out)
  n_in <- length(players_in)
  n_pair <- min(n_out, n_in)

  tibble(
    trade_seq = seq_len(n_pair),
    player_out_id = if (n_pair > 0) players_out[seq_len(n_pair)] else integer(),
    player_in_id = if (n_pair > 0) players_in[seq_len(n_pair)] else integer()
  )
}

get_settings <- function() {
  sc_get_json("/settings")
}

get_me <- function() {
  sc_get_json("/me")
}

get_teams <- function() {
  sc_get_json("/teams")
}

get_ladder_fixtures_round <- function(round_value) {
  x <- sc_get_json(
    paste0("/leagues/", league_id, "/ladderAndFixtures"),
    query = list(round = round_value)
  )

  ladder_tbl <- purrr::map_dfr(x$ladder %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      league_id = safe_int(z$league_id, league_id),
      round = safe_int(z$round, round_value),
      user_team_id = safe_int(z$user_team_id),
      team_name = safe_chr(z$userTeam$teamname),
      coach_name = safe_chr(z$userTeam$user$first_name),
      is_me = safe_lgl(z$userTeam$user$is_me, FALSE),
      wins = safe_dbl(z$wins),
      losses = safe_dbl(z$losses),
      draws = safe_dbl(z$draws),
      ladder_points = safe_dbl(z$points),
      points_for = safe_dbl(z$points_for),
      points_against = safe_dbl(z$points_against),
      position = safe_dbl(z$position),
      last_position = safe_dbl(z$last_position),
      wins_last5 = safe_dbl(z$wins_last5),
      losses_last5 = safe_dbl(z$losses_last5),
      draws_last5 = safe_dbl(z$draws_last5),
      round_points = safe_dbl(z$userTeam$stats[[1]]$points),
      total_points = safe_dbl(z$userTeam$stats[[1]]$total_points),
      overall_position = safe_dbl(z$userTeam$stats[[1]]$position),
      round_position = safe_dbl(z$userTeam$stats[[1]]$round_position),
      squad_value = safe_dbl(z$userTeam$stats[[1]]$price),
      price_change = safe_dbl(z$userTeam$stats[[1]]$price_change),
      total_price_change = safe_dbl(z$userTeam$stats[[1]]$total_price_change),
      rounds_played = safe_dbl(z$userTeam$stats[[1]]$rounds_played)
    )
  })

  fixtures_tbl <- purrr::map_dfr(x$fixtures %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      league_id = league_id,
      round = safe_int(z$round, round_value),
      fixture = safe_int(z$fixture),
      fixture_id = paste0("league_", safe_int(z$round, round_value), "_", safe_int(z$fixture)),
      user_team1_id = safe_int(z$user_team1$id),
      user_team1_name = safe_chr(z$user_team1$teamname),
      user_team1_coach = safe_chr(z$user_team1$user$first_name),
      user_team1_points = safe_dbl(z$user_team1$stats[[1]]$points),
      user_team2_id = safe_int(z$user_team2$id),
      user_team2_name = safe_chr(z$user_team2$teamname),
      user_team2_coach = safe_chr(z$user_team2$user$first_name),
      user_team2_points = safe_dbl(z$user_team2$stats[[1]]$points)
    )
  })

  list(ladder = ladder_tbl, fixtures = fixtures_tbl)
}

get_stats_players_round <- function(team_id, round_value) {
  x <- sc_get_json(
    paste0("/userteams/", team_id, "/statsPlayers"),
    query = list(round = round_value)
  )

  players_tbl <- purrr::map_dfr(x$players %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      user_team_id = safe_int(z$user_team_id, team_id),
      round = safe_int(z$round, round_value),
      player_id = safe_int(z$player_id),
      picked = safe_lgl(z$picked, FALSE),
      position = safe_chr(z$position),
      updated = safe_chr(z$updated),
      position_long = safe_chr(z$position_long),
      position_sort = safe_int(z$position_sort)
    )
  })

  stats_tbl <- purrr::map_dfr(x$stats %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      user_team_id = safe_int(z$user_team_id, team_id),
      round = safe_int(z$round, round_value),
      salarycap = safe_dbl(z$salarycap),
      points = safe_dbl(z$points),
      total_points = safe_dbl(z$total_points),
      position = safe_dbl(z$position),
      last_position = safe_dbl(z$last_position),
      round_position = safe_dbl(z$round_position),
      price = safe_dbl(z$price),
      price_change = safe_dbl(z$price_change),
      total_price_change = safe_dbl(z$total_price_change),
      rounds_played = safe_dbl(z$rounds_played),
      changes = safe_int(z$changes),
      total_changes = safe_int(z$total_changes),
      trade_boosts_used = safe_int(z$trade_boosts_used),
      last_trade_boosts_used = safe_int(z$last_trade_boosts_used),
      league_wins = safe_int(z$league_wins),
      league_draws = safe_int(z$league_draws),
      league_losses = safe_int(z$league_losses)
    )
  })

  trades_tbl <- purrr::map_dfr(x$trades %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      round = safe_int(z$round, round_value),
      user_team_id = safe_int(z$user_id, team_id),
      buy_player_id = safe_int(z$buy_player_id),
      sell_player_id = safe_int(z$sell_player_id),
      trade_source = "actual_api"
    )
  })

  list(players = players_tbl, stats = stats_tbl, trades = trades_tbl)
}

extract_initialvalue_catalog <- function(year = season_year) {
  x <- stats_get_json(
    "https://www.nrlsupercoachstats.com/initialvalue.php",
    query = list(
      year = year,
      grid_id = "list1",
      jqgrid_page = 1,
      rows = 2000,
      search = "false"
    )
  )

  rows <- bind_rows(x$rows %||% list())
  rows %>%
    transmute(
      player_name = Name %>%
        gsub("^.*?>", "", .) %>%
        gsub("</a>$", "", .),
      team_abbrev = Team,
      posn1 = Posn1,
      posn2 = ifelse(Posn2 == "", NA_character_, Posn2),
      positions = ifelse(is.na(posn2), posn1, paste(posn1, posn2, sep = "/")),
      current_price_external = suppressWarnings(as.numeric(Price)),
      avg_score_external = suppressWarnings(as.numeric(AvgScore)),
      projected_price_next = suppressWarnings(as.numeric(ProjectedPrice))
    ) %>%
    distinct(player_name, .keep_all = TRUE) %>%
    arrange(player_name)
}

get_yearplot_player <- function(player_name, year = season_year) {
  stats_get_json(
    "https://www.nrlsupercoachstats.com/highcharts/data-yearplot.php",
    query = list(dropdown1 = player_name, YEAR = year)
  )
}

yearplot_to_tibble_year <- function(x, player_name, year = season_year) {
  if (length(x) == 0) {
    return(tibble(
      player_name = character(),
      year = integer(),
      round = integer(),
      score = numeric(),
      mins = numeric(),
      price = numeric()
    ))
  }

  rounds <- suppressWarnings(as.integer(unlist(x[[1]]$data)))
  out <- tibble(player_name = player_name, year = year, round = rounds)

  for (i in seq_along(x)[-1]) {
    nm <- safe_chr(x[[i]]$name, "")
    vals <- suppressWarnings(as.numeric(unlist(x[[i]]$data)))

    if (identical(nm, paste0(year, "Score"))) out$score <- vals
    if (identical(nm, paste0(year, "Mins"))) out$mins <- vals
    if (identical(nm, paste0(year, "Price"))) out$price <- vals
  }

  out
}

safe_get_price_history <- function(player_name, year = season_year) {
  tryCatch(
    {
      get_yearplot_player(player_name, year) %>%
        yearplot_to_tibble_year(player_name = player_name, year = year)
    },
    error = function(e) {
      tibble(
        player_name = player_name,
        year = year,
        round = integer(),
        score = numeric(),
        mins = numeric(),
        price = numeric()
      )
    }
  )
}

print_results <- function(x, n = 10) {
  print(utils::head(as.data.frame(x), n = n), row.names = FALSE)
}
```

## 4. Empty table templates

```{r}
empty_ladder_history <- tibble(
  run_ts = as.POSIXct(character()),
  league_id = integer(),
  round = integer(),
  user_team_id = integer()
)

empty_fixtures_history <- tibble(
  run_ts = as.POSIXct(character()),
  league_id = integer(),
  round = integer(),
  fixture = integer(),
  fixture_id = character()
)

empty_team_players_snapshots <- tibble(
  run_ts = as.POSIXct(character()),
  user_team_id = integer(),
  round = integer(),
  player_id = integer()
)

empty_team_players_latest <- empty_team_players_snapshots

empty_team_round_signatures <- tibble(
  run_ts = as.POSIXct(character()),
  league_id = integer(),
  user_team_id = integer(),
  round = integer(),
  roster_signature = character()
)

empty_team_round_stats_history <- tibble(
  run_ts = as.POSIXct(character()),
  user_team_id = integer(),
  round = integer(),
  total_changes = integer(),
  trade_boosts_used = integer()
)

empty_actual_trade_history <- tibble(
  run_ts = as.POSIXct(character()),
  round = integer(),
  user_team_id = integer(),
  buy_player_id = integer(),
  sell_player_id = integer(),
  trade_source = character()
)

empty_inferred_changes <- tibble(
  detected_run_ts = as.POSIXct(character()),
  from_run_ts = as.POSIXct(character()),
  to_run_ts = as.POSIXct(character()),
  league_id = integer(),
  user_team_id = integer(),
  round = integer(),
  players_out = list(),
  players_in = list(),
  players_out_n = integer(),
  players_in_n = integer(),
  inferred_trade_pairs = list()
)

empty_run_log <- tibble(
  run_ts = as.POSIXct(character()),
  league_id = integer(),
  first_run = logical(),
  current_round = integer(),
  rounds_pulled = character(),
  ladder_rows_new = integer(),
  player_snapshot_rows_new = integer(),
  changed_team_rounds = integer(),
  failed_team_rounds = integer()
)

empty_player_price_history_2026 <- tibble(
  player_name = character(),
  year = integer(),
  round = integer(),
  score = numeric(),
  mins = numeric(),
  price = numeric()
)
```

## 5. Load existing history

```{r}
ladder_history_existing <- read_rds_if_exists(path_ladder_history, empty_ladder_history)
fixtures_history_existing <- read_rds_if_exists(path_fixtures_history, empty_fixtures_history)
team_players_snapshots_existing <- read_rds_if_exists(path_team_players_snapshots, empty_team_players_snapshots)
team_players_latest_existing <- read_rds_if_exists(path_team_players_latest, empty_team_players_latest)
team_round_signatures_existing <- read_rds_if_exists(path_team_round_signatures, empty_team_round_signatures)
team_round_stats_history_existing <- read_rds_if_exists(path_team_round_stats_history, empty_team_round_stats_history)
actual_trade_history_existing <- read_rds_if_exists(path_actual_trade_history, empty_actual_trade_history)
inferred_changes_existing <- read_rds_if_exists(path_inferred_changes, empty_inferred_changes)
run_log_existing <- read_rds_if_exists(path_run_log, empty_run_log)
player_price_history_existing <- read_rds_if_exists(path_player_price_history_2026, empty_player_price_history_2026)
```

## 6. Reference data and round state

```{r}
settings <- get_settings()
me_profile <- get_me()
teams_reference <- bind_rows_safe(get_teams()) %>%
  transmute(
    team_id = as.integer(id),
    team_abbrev = as.character(abbrev),
    team_feed_name = as.character(feed_name),
    team_name = as.character(name)
  )

current_round <- safe_int(settings$competition$current_round)
next_round <- safe_int(settings$competition$next_round)
competition_status <- safe_chr(settings$competition$status)

if (is.na(current_round)) {
  stop("Could not detect current round from /settings")
}

first_run <- nrow(ladder_history_existing) == 0 || nrow(team_round_signatures_existing) == 0
```

## 7. Pull ladder, fixtures, team-round rosters and stats

```{r}
rounds_to_pull <- if (first_run) seq_len(current_round) else current_round

ladder_pulls <- map(rounds_to_pull, get_ladder_fixtures_round)

ladder_history_new <- map_dfr(ladder_pulls, "ladder")
fixtures_history_new <- map_dfr(ladder_pulls, "fixtures")

ladder_history <- bind_rows(ladder_history_existing, ladder_history_new) %>%
  arrange(run_ts, round, position, user_team_id)

fixtures_history <- bind_rows(fixtures_history_existing, fixtures_history_new) %>%
  distinct(run_ts, fixture_id, .keep_all = TRUE) %>%
  arrange(run_ts, round, fixture)

team_lookup <- ladder_history %>%
  distinct(user_team_id, team_name, coach_name, is_me) %>%
  filter(!is.na(user_team_id))

grog_baguettes_team_id <- team_lookup %>%
  filter(is_me %in% TRUE) %>%
  distinct(user_team_id) %>%
  pull(user_team_id) %>%
  first()

team_round_grid <- ladder_history_new %>%
  distinct(user_team_id, round) %>%
  filter(!is.na(user_team_id), !is.na(round)) %>%
  arrange(round, user_team_id)

grid_records <- split(team_round_grid, seq_len(nrow(team_round_grid)))

team_pull_list <- parallel_map(
  grid_records,
  function(row_df) {
    team_id <- row_df$user_team_id[[1]]
    round_value <- row_df$round[[1]]

    tryCatch(
      get_stats_players_round(team_id, round_value),
      error = function(e) {
        list(
          players = tibble(),
          stats = tibble(),
          trades = tibble(),
          error = conditionMessage(e)
        )
      }
    )
  }
)

team_players_pull <- if (nrow(team_round_grid) == 0) {
  team_round_grid %>%
    mutate(
      pull = list(),
      players = list(),
      stats = list(),
      trades = list(),
      pull_error = character(),
      pull_ok = logical()
    )
} else {
  team_round_grid %>%
    mutate(
      pull = team_pull_list,
      players = map(pull, "players"),
      stats = map(pull, "stats"),
      trades = map(pull, "trades"),
      pull_error = map_chr(pull, ~ .x$error %||% NA_character_),
      pull_ok = map_lgl(pull, ~ is.null(.x$error))
    )
}

team_round_stats_history_new <- team_players_pull %>%
  select(stats) %>%
  unnest(stats)

actual_trade_history_new <- team_players_pull %>%
  select(trades) %>%
  unnest(trades)

team_round_stats_history <- bind_rows(
  team_round_stats_history_existing,
  team_round_stats_history_new
) %>%
  distinct(run_ts, user_team_id, round, .keep_all = TRUE) %>%
  arrange(run_ts, round, user_team_id)

actual_trade_history <- bind_rows(
  actual_trade_history_existing,
  actual_trade_history_new
) %>%
  distinct(round, user_team_id, buy_player_id, sell_player_id, .keep_all = TRUE) %>%
  arrange(round, user_team_id, buy_player_id, sell_player_id)
```

## 8. Build snapshot signatures and protect reruns

```{r}
latest_existing_signatures <- team_round_signatures_existing %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(user_team_id, round, prev_run_ts = run_ts, prev_roster_signature = roster_signature)

team_round_results <- team_players_pull %>%
  mutate(
    roster_signature = map_chr(players, build_roster_signature),
    player_rows = map_int(players, nrow)
  ) %>%
  left_join(
    latest_existing_signatures,
    by = c("user_team_id", "round")
  ) %>%
  mutate(
    is_valid_roster_pull = pull_ok & !is.na(roster_signature) & player_rows > 0,
    is_new_snapshot = case_when(
      !is_valid_roster_pull ~ FALSE,
      is.na(prev_roster_signature) ~ TRUE,
      roster_signature != prev_roster_signature ~ TRUE,
      TRUE ~ FALSE
    )
  )

team_round_signatures_new <- team_round_results %>%
  filter(is_new_snapshot) %>%
  transmute(
    run_ts = run_ts,
    league_id = league_id,
    user_team_id,
    round,
    roster_signature
  )

team_players_snapshots_new <- team_round_results %>%
  filter(is_new_snapshot) %>%
  select(players) %>%
  unnest(players)
```

## 9. Append snapshots, rebuild latest team state, and infer changes

```{r}
team_round_signatures <- bind_rows(
  team_round_signatures_existing,
  team_round_signatures_new
) %>%
  arrange(run_ts, round, user_team_id)

team_players_snapshots <- bind_rows(
  team_players_snapshots_existing,
  team_players_snapshots_new
) %>%
  arrange(run_ts, round, user_team_id, position_sort, player_id)

latest_snapshot_per_team_round <- team_round_signatures %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(user_team_id, round, latest_run_ts = run_ts)

team_players_latest <- team_players_snapshots %>%
  inner_join(
    latest_snapshot_per_team_round,
    by = c("user_team_id", "round")
  ) %>%
  filter(run_ts == latest_run_ts) %>%
  select(-latest_run_ts) %>%
  arrange(user_team_id, round, position_sort, position, player_id)

previous_membership_lookup <- team_round_signatures_existing %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(user_team_id, round, prev_run_ts = run_ts)

previous_membership_source <- previous_membership_lookup %>%
  inner_join(
    team_players_snapshots_existing,
    by = c("user_team_id", "round", "prev_run_ts" = "run_ts")
  )

previous_membership <- if (nrow(previous_membership_source) == 0) {
  tibble(
    user_team_id = integer(),
    round = integer(),
    prev_run_ts = as.POSIXct(character()),
    prev_players = list()
  )
} else {
  previous_membership_source %>%
    group_by(user_team_id, round, prev_run_ts) %>%
    group_modify(~ tibble(prev_players = list(extract_roster_membership(.x)))) %>%
    ungroup()
}

current_membership <- team_round_results %>%
  filter(is_new_snapshot) %>%
  transmute(
    user_team_id,
    round,
    detected_run_ts = run_ts,
    from_run_ts = prev_run_ts,
    to_run_ts = run_ts,
    current_players = map(players, extract_roster_membership)
  )

inferred_changes_new <- current_membership %>%
  left_join(previous_membership, by = c("user_team_id", "round", "from_run_ts" = "prev_run_ts")) %>%
  mutate(
    prev_players = map(prev_players, ~ if (is.null(.x)) tibble(player_id = integer()) else .x),
    players_in_tbl = map2(current_players, prev_players, ~ anti_join(.x, .y, by = "player_id")),
    players_out_tbl = map2(prev_players, current_players, ~ anti_join(.x, .y, by = "player_id")),
    players_in = map(players_in_tbl, ~ .x$player_id),
    players_out = map(players_out_tbl, ~ .x$player_id),
    players_in_n = map_int(players_in, length),
    players_out_n = map_int(players_out, length),
    inferred_trade_pairs = map2(players_out, players_in, pair_inferred_trades)
  ) %>%
  transmute(
    detected_run_ts,
    from_run_ts,
    to_run_ts,
    league_id = league_id,
    user_team_id,
    round,
    players_out,
    players_in,
    players_out_n,
    players_in_n,
    inferred_trade_pairs
  )

inferred_changes <- bind_rows(
  inferred_changes_existing,
  inferred_changes_new
) %>%
  arrange(to_run_ts, round, user_team_id)
```

## 10. Save core league outputs

```{r}
run_log <- bind_rows(
  run_log_existing,
  tibble(
    run_ts = run_ts,
    league_id = league_id,
    first_run = first_run,
    current_round = current_round,
    rounds_pulled = paste(rounds_to_pull, collapse = ","),
    ladder_rows_new = nrow(ladder_history_new),
    player_snapshot_rows_new = nrow(team_players_snapshots_new),
    changed_team_rounds = nrow(team_round_signatures_new),
    failed_team_rounds = sum(!team_round_results$pull_ok)
  )
)

saveRDS(ladder_history, path_ladder_history)
saveRDS(fixtures_history, path_fixtures_history)
saveRDS(team_players_snapshots, path_team_players_snapshots)
saveRDS(team_players_latest, path_team_players_latest)
saveRDS(team_round_signatures, path_team_round_signatures)
saveRDS(team_round_stats_history, path_team_round_stats_history)
saveRDS(actual_trade_history, path_actual_trade_history)
saveRDS(inferred_changes, path_inferred_changes)
saveRDS(run_log, path_run_log)

grog_baguettes_latest <- team_players_latest %>%
  filter(user_team_id == grog_baguettes_team_id)

grog_baguettes_changes <- inferred_changes %>%
  filter(user_team_id == grog_baguettes_team_id) %>%
  arrange(desc(to_run_ts))

league_change_summary <- inferred_changes %>%
  left_join(
    team_lookup %>% distinct(user_team_id, team_name, coach_name),
    by = "user_team_id"
  ) %>%
  arrange(desc(to_run_ts), round, team_name)
```

## 11. Pull player reference data and external price history

```{r}
players_cf_list <- sc_get_json("/players-cf")

player_catalog <- tibble(
  player_id = map_int(players_cf_list, ~ safe_int(.x$id)),
  first_name = map_chr(players_cf_list, ~ safe_chr(.x$first_name)),
  last_name = map_chr(players_cf_list, ~ safe_chr(.x$last_name)),
  full_name = paste(last_name, first_name, sep = ", "),
  name_norm = normalise_player_name(full_name),
  team_id = map_int(players_cf_list, ~ safe_int(.x$team_id)),
  team_abbrev = map_chr(players_cf_list, ~ safe_chr(.x$team$abbrev)),
  team_name = map_chr(players_cf_list, ~ safe_chr(.x$team$name)),
  locked_flag = map_lgl(players_cf_list, ~ safe_lgl(.x$locked, FALSE)),
  played_status = map_chr(players_cf_list, ~ safe_chr(.x$played_status$status)),
  played_status_display = map_chr(players_cf_list, ~ safe_chr(.x$played_status$display)),
  active_flag = map_lgl(players_cf_list, ~ safe_lgl(.x$active, FALSE)),
  injury_suspension_status = map_chr(players_cf_list, ~ safe_chr(.x$injury_suspension_status)),
  injury_suspension_status_text = map_chr(players_cf_list, ~ safe_chr(.x$injury_suspension_status_text))
)

players_cf_2026 <- player_catalog
player_id_lookup <- player_catalog %>%
  select(player_id, full_name, team_abbrev, team_name)

initialvalue_catalog <- extract_initialvalue_catalog(season_year) %>%
  mutate(name_norm = normalise_player_name(player_name))

existing_players_2026 <- player_price_history_existing %>%
  filter(year == season_year) %>%
  distinct(player_name) %>%
  pull(player_name)

players_to_fetch <- setdiff(initialvalue_catalog$player_name, existing_players_2026)

player_price_history_new <- if (length(players_to_fetch) == 0) {
  empty_player_price_history_2026
} else {
  bind_rows(parallel_map(players_to_fetch, safe_get_price_history))
}

player_price_history_2026 <- bind_rows(
  player_price_history_existing,
  player_price_history_new
) %>%
  filter(year == season_year) %>%
  distinct(player_name, year, round, .keep_all = TRUE) %>%
  arrange(player_name, round)

saveRDS(player_price_history_2026, path_player_price_history_2026)
saveRDS(players_cf_2026, path_players_cf_2026)
saveRDS(player_id_lookup, path_player_id_lookup)
```

## 12. Crosswalk yearplot histories to SuperCoach player ids

```{r}
player_crosswalk_primary <- initialvalue_catalog %>%
  inner_join(
    player_catalog %>% select(player_id, full_name, name_norm, team_abbrev),
    by = c("name_norm", "team_abbrev")
  ) %>%
  distinct(player_name, player_id, .keep_all = TRUE)

unmatched_initialvalue <- initialvalue_catalog %>%
  anti_join(player_crosswalk_primary, by = c("player_name", "team_abbrev", "name_norm"))

player_crosswalk_fallback <- unmatched_initialvalue %>%
  inner_join(
    player_catalog %>%
      count(name_norm, name = "sc_name_matches") %>%
      filter(sc_name_matches == 1) %>%
      inner_join(player_catalog %>% select(player_id, full_name, name_norm, team_abbrev), by = "name_norm"),
    by = "name_norm"
  ) %>%
  distinct(player_name, player_id, .keep_all = TRUE)

player_crosswalk <- bind_rows(player_crosswalk_primary, player_crosswalk_fallback) %>%
  distinct(player_name, player_id, .keep_all = TRUE)

player_price_history_sc <- player_price_history_2026 %>%
  inner_join(
    player_crosswalk %>% select(player_name, player_id),
    by = "player_name"
  ) %>%
  transmute(
    player_id,
    player_name,
    year,
    round,
    score,
    mins,
    price
  ) %>%
  distinct(player_id, round, .keep_all = TRUE) %>%
  arrange(player_id, round)

price_match_discrepancies <- team_players_latest %>%
  distinct(user_team_id, round, player_id) %>%
  anti_join(
    player_price_history_sc %>% distinct(player_id, round),
    by = c("player_id", "round")
  ) %>%
  left_join(player_id_lookup, by = "player_id") %>%
  arrange(round, user_team_id, player_id)

if (nrow(price_match_discrepancies) > 0) {
  print_results(price_match_discrepancies)
  stop("Stopping: unmatched in-league player_id/round combinations remain in player_price_history_sc")
}

saveRDS(player_price_history_sc, path_player_price_history_sc)
```

## 13. Build lookup tables from confirmed sources

```{r}
player_price_rollups <- player_price_history_sc %>%
  arrange(player_id, round) %>%
  group_by(player_id) %>%
  mutate(
    season_average = cumsum(coalesce(score, 0)) / seq_along(score),
    avg_3 = roll_mean_right(score, 3),
    avg_5 = roll_mean_right(score, 5),
    volatility_score = roll_sd_right(score, 5),
    floor_score_estimate = roll_min_right(score, 5),
    ceiling_score_estimate = roll_max_right(score, 5),
    games_played = cumsum(!is.na(score)),
    total_points = cumsum(coalesce(score, 0)),
    price_change_last_round = price - lag(price),
    cumulative_cash_generation = price - first(price)
  ) %>%
  ungroup()

latest_price_rollups <- player_price_rollups %>%
  group_by(player_id) %>%
  slice_max(round, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(
    player_id,
    latest_round = round,
    current_price_history = price,
    season_average,
    avg_3,
    avg_5,
    games_played,
    total_points,
    price_change_last_round,
    cumulative_cash_generation
  )

player_history_lists <- player_price_history_sc %>%
  arrange(player_id, round) %>%
  group_by(player_id) %>%
  summarise(
    points_history = list(tibble(round = round, score = score)),
    minute_history = list(tibble(round = round, mins = mins)),
    price_history = list(tibble(round = round, price = price)),
    .groups = "drop"
  )

master_player_round_latest <- player_catalog %>%
  left_join(initialvalue_catalog, by = c("full_name" = "player_name", "team_abbrev", "name_norm")) %>%
  left_join(latest_price_rollups, by = "player_id") %>%
  left_join(player_history_lists, by = "player_id") %>%
  transmute(
    run_ts = run_ts,
    player_id,
    full_name,
    team = coalesce(team_abbrev, team_name),
    positions = positions,
    current_price = coalesce(current_price_history, current_price_external),
    breakeven = NA_real_,
    current_season_average = season_average,
    average_3_round = avg_3,
    average_5_round = avg_5,
    ownership_percentage = NA_real_,
    total_points,
    games_played,
    status = case_when(
      !is.na(injury_suspension_status_text) ~ injury_suspension_status_text,
      !active_flag ~ "inactive",
      TRUE ~ played_status_display
    ),
    injury_detail = injury_suspension_status_text,
    expected_return = NA_character_,
    role_tag = NA_character_,
    goal_kicking_status = NA_character_,
    starting_status = NA_character_,
    locked_flag,
    played_status,
    active_flag,
    minute_history,
    points_history,
    price_history
  )

player_scoring_component_history <- player_price_rollups %>%
  transmute(
    run_ts = run_ts,
    player_id,
    round,
    total_score = score,
    base_stats = NA_real_,
    base_attack = NA_real_,
    tries = NA_real_,
    try_assists = NA_real_,
    linebreaks = NA_real_,
    linebreak_assists = NA_real_,
    tackle_busts = NA_real_,
    offloads = NA_real_,
    goals = NA_real_,
    kick_metres = NA_real_,
    tackles_made = NA_real_,
    missed_tackles = NA_real_,
    run_metres = NA_real_,
    errors = NA_real_,
    disruptions = NA_character_,
    minutes_played = mins,
    starting_position_that_round = NA_character_,
    base_per_minute = NA_real_,
    attack_reliance_ratio = NA_real_,
    volatility_score = volatility_score,
    floor_score_estimate = floor_score_estimate,
    ceiling_score_estimate = ceiling_score_estimate,
    role_adjusted_average = NA_real_,
    points_per_minute = if_else(!is.na(mins) & mins > 0, score / mins, NA_real_)
  )

availability_risk_table <- player_catalog %>%
  transmute(
    run_ts = run_ts,
    player_id,
    full_name,
    team_abbrev,
    locked_flag,
    played_status,
    played_status_display,
    active_flag,
    injury_suspension_status,
    injury_suspension_status_text,
    expected_return = NA_character_,
    risk_band = case_when(
      !is.na(injury_suspension_status) ~ "high",
      active_flag & locked_flag ~ "medium",
      active_flag ~ "low",
      TRUE ~ "high"
    )
  )

my_round_state <- team_round_stats_history %>%
  filter(user_team_id == grog_baguettes_team_id) %>%
  group_by(round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup()

position_rules_tbl <- bind_rows_safe(settings$game$positions) %>%
  transmute(
    position_id = as.character(id),
    position_name = as.character(name),
    position_sort = as.integer(sort),
    max_players = as.integer(max_players),
    active_max_players = as.integer(active_max_players)
  )

game_rules_round_state <- tibble(
  run_ts = run_ts,
  league_id = league_id,
  current_round = current_round,
  next_round = next_round,
  competition_status = competition_status,
  is_lockout = safe_lgl(settings$competition$is_lockout, FALSE),
  is_partial_lockout = safe_lgl(settings$competition$is_partial_lockout, FALSE),
  lockout_start = safe_chr(settings$competition$lockout_start),
  lockout_end = safe_chr(settings$competition$lockout_end),
  rolling_lockout = safe_lgl(settings$game$rolling_lockout, FALSE),
  squad_size = safe_int(settings$game$max_players_for_team),
  selected_slots = sum(position_rules_tbl$active_max_players, na.rm = TRUE) + safe_int(settings$game$game_num_emergencies, 0L),
  emergency_slots = safe_int(settings$game$game_num_emergencies),
  max_total_trades = safe_int(settings$game$game_max_total_changes),
  max_round_trades_without_boost = safe_int(settings$game$game_max_changes),
  trades_used_to_date = my_round_state %>% filter(round == current_round) %>% pull(total_changes) %>% { if (length(.) == 0) NA_integer_ else .[[1]] },
  trades_remaining = safe_int(settings$game$game_max_total_changes) - coalesce(
    my_round_state %>% filter(round == current_round) %>% pull(total_changes) %>% { if (length(.) == 0) NA_integer_ else .[[1]] },
    0L
  ),
  max_boosts = safe_int(settings$game$max_boosts),
  boosts_used_to_date = my_round_state %>% filter(round == current_round) %>% pull(trade_boosts_used) %>% { if (length(.) == 0) NA_integer_ else .[[1]] },
  boosts_remaining = safe_int(settings$game$max_boosts) - coalesce(
    my_round_state %>% filter(round == current_round) %>% pull(trade_boosts_used) %>% { if (length(.) == 0) NA_integer_ else .[[1]] },
    0L
  ),
  dual_position_enabled = safe_lgl(settings$game$dual_position_players, FALSE),
  bye_round_structure = list(unlist(settings$game$show_bye_rounds %||% list())),
  real_bye_rounds = list(unlist(settings$game$real_bye_rounds %||% list())),
  finals_round = safe_int(settings$game$game_finals_round),
  scoring_round_end = safe_int(settings$game$final_scoring_round),
  price_rounding = safe_int(settings$game$rounding_price),
  position_rules = list(position_rules_tbl),
  player_lock_state = list(availability_risk_table %>% select(player_id, full_name, locked_flag, played_status, played_status_display))
)

fixture_triggers <- tibble(
  run_ts = run_ts,
  current_round = current_round,
  next_round = next_round,
  lockout_start = safe_chr(settings$competition$lockout_start),
  lockout_end = safe_chr(settings$competition$lockout_end),
  competition_status = competition_status
)

team_list_role_certainty <- team_players_latest %>%
  left_join(
    player_price_history_sc %>%
      group_by(player_id) %>%
      arrange(round, .by_group = TRUE) %>%
      mutate(likely_minutes = roll_mean_right(mins, 3)) %>%
      ungroup() %>%
      select(player_id, round, mins, likely_minutes),
    by = c("player_id", "round")
  ) %>%
  mutate(
    named_flag = TRUE,
    jersey_number = if_else(!is.na(position_sort), as.integer(position_sort), NA_integer_),
    starting_or_bench = case_when(
      !is.na(position_sort) & position_sort <= 17 ~ "selected",
      !is.na(position_sort) & position_sort > 17 ~ "reserve",
      TRUE ~ "unknown"
    ),
    listed_position = position,
    actual_recent_role = position_long,
    role_change_likelihood = case_when(
      !is.na(likely_minutes) & likely_minutes < 25 ~ "high",
      !is.na(likely_minutes) & likely_minutes < 45 ~ "medium",
      !is.na(likely_minutes) ~ "low",
      TRUE ~ NA_character_
    ),
    likely_late_omission = NA_character_,
    likely_replacement = NA_character_,
    injury_cover_flag = NA,
    return_threat_flag = NA
  ) %>%
  select(
    run_ts, user_team_id, round, player_id, named_flag, jersey_number,
    starting_or_bench, listed_position, actual_recent_role, likely_minutes,
    role_change_likelihood, likely_late_omission, likely_replacement,
    injury_cover_flag, return_threat_flag
  )

fixture_matchup_table <- tibble(
  run_ts = as.POSIXct(character()),
  round = integer(),
  team_abbrev = character(),
  opponent = character(),
  venue = character(),
  home_away = character(),
  days_rest = numeric(),
  travel_burden = character(),
  short_turnaround_flag = logical(),
  opponent_recent_form = numeric(),
  team_recent_form = numeric(),
  projected_game_total = numeric(),
  projected_team_scoring_environment = numeric(),
  opponent_defensive_weakness_by_position = character(),
  opponent_attacking_weakness_by_position = character(),
  team_style_indicator = character(),
  bye_flag = logical(),
  major_outs_opponent = character(),
  major_outs_team = character(),
  matchup_rating_by_player = numeric(),
  matchup_rating_by_team = numeric(),
  next_2_rounds_difficulty = numeric(),
  next_3_rounds_difficulty = numeric(),
  next_5_rounds_difficulty = numeric(),
  schedule_swing_indicator = character()
)

team_performance_context <- tibble(
  run_ts = as.POSIXct(character()),
  team_abbrev = character(),
  round = integer(),
  points_scored = numeric(),
  points_conceded = numeric(),
  tries_scored = numeric(),
  tries_conceded = numeric(),
  linebreaks_for = numeric(),
  linebreaks_against = numeric(),
  possession_share = numeric(),
  territory_indicators = character(),
  completion_rate = numeric(),
  attacking_trend_last_3 = numeric(),
  attacking_trend_last_5 = numeric(),
  defensive_trend_last_3 = numeric(),
  defensive_trend_last_5 = numeric(),
  left_edge_vulnerability = numeric(),
  right_edge_vulnerability = numeric(),
  middle_defensive_weakness = numeric()
)

cash_generation_model <- player_catalog %>%
  left_join(initialvalue_catalog, by = c("full_name" = "player_name", "team_abbrev", "name_norm")) %>%
  left_join(latest_price_rollups, by = "player_id") %>%
  transmute(
    run_ts = run_ts,
    player_id,
    full_name,
    team_abbrev,
    starting_price = current_price_external,
    current_price = coalesce(current_price_history, current_price_external),
    price_change_last_round,
    cumulative_cash_generation,
    projected_price_rise_next_round = projected_price_next - coalesce(current_price_history, current_price_external),
    projected_price_fall_next_round = if_else(projected_price_next < coalesce(current_price_history, current_price_external), projected_price_next - coalesce(current_price_history, current_price_external), 0),
    breakeven_trend = NA_real_,
    games_until_peak_cash_estimate = NA_real_,
    cash_cow_maturity_status = case_when(
      !is.na(projected_price_next) & projected_price_next > coalesce(current_price_history, current_price_external) ~ "rising",
      !is.na(projected_price_next) & projected_price_next <= coalesce(current_price_history, current_price_external) ~ "near_peak_or_peaked",
      TRUE ~ NA_character_
    ),
    player_classification = case_when(
      !is.na(current_price_external) & current_price_external <= 350000 ~ "cash_cow",
      !is.na(current_price_external) & current_price_external >= 700000 ~ "keeper",
      !is.na(current_price_external) ~ "stepping_stone",
      TRUE ~ NA_character_
    )
  )

squad_round_enriched <- team_players_latest %>%
  left_join(
    player_price_rollups %>%
      select(player_id, round, score, mins, price, avg_3, avg_5),
    by = c("player_id", "round")
  ) %>%
  left_join(
    team_lookup %>% select(user_team_id, team_name, coach_name, is_me),
    by = "user_team_id"
  ) %>%
  left_join(
    master_player_round_latest %>%
      select(player_id, full_name, positions, locked_flag, status),
    by = "player_id"
  ) %>%
  group_by(user_team_id, player_id) %>%
  mutate(
    acquisition_round = min(round, na.rm = TRUE),
    acquisition_price = price[match(acquisition_round, round)],
    profit_or_loss = price - acquisition_price
  ) %>%
  ungroup() %>%
  mutate(
    current_role_security = case_when(
      !is.na(mins) & mins >= 50 ~ "high",
      !is.na(mins) & mins >= 30 ~ "medium",
      !is.na(mins) ~ "low",
      TRUE ~ NA_character_
    ),
    keeper_status = case_when(
      !is.na(price) & price >= 700000 ~ "keeper",
      !is.na(price) ~ "non_keeper",
      TRUE ~ NA_character_
    ),
    sell_urgency = case_when(
      status %in% c("Out", "Suspended") ~ "high",
      TRUE ~ "normal"
    ),
    cover_value = case_when(
      str_detect(coalesce(positions, ""), "/") ~ "high",
      TRUE ~ "standard"
    ),
    captaincy_value = avg_3,
    bye_usefulness = NA_real_,
    dpp_flexibility_usefulness = if_else(str_detect(coalesce(positions, ""), "/"), 1, 0),
    injury_suspension_risk = status,
    currently_locked = locked_flag,
    selected_this_week = !is.na(position_sort) & position_sort <= 17,
    field_bench_npr = case_when(
      !is.na(position_sort) & position_sort <= 13 ~ "field",
      !is.na(position_sort) & position_sort <= 17 ~ "bench",
      !is.na(position_sort) ~ "npr",
      TRUE ~ NA_character_
    ),
    projected_score_this_week = avg_3,
    projected_score_next_3_weeks = avg_5,
    projected_value_change_next_3_weeks = NA_real_
  ) %>%
  select(
    run_ts, user_team_id, team_name, coach_name, is_me, round, player_id, full_name,
    acquisition_round, acquisition_price, current_price = price, profit_or_loss,
    current_role_security, keeper_status, sell_urgency, cover_value, captaincy_value,
    bye_usefulness, dpp_flexibility_usefulness, injury_suspension_risk,
    currently_locked, selected_this_week, field_bench_npr, projected_score_this_week,
    projected_score_next_3_weeks, projected_value_change_next_3_weeks
  )

latest_team_round_stats <- team_round_stats_history %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup()

opponent_behaviour_history <- team_players_latest %>%
  group_by(user_team_id, round) %>%
  summarise(
    squad_player_ids = list(sort(unique(player_id))),
    .groups = "drop"
  ) %>%
  left_join(
    inferred_changes %>%
      group_by(user_team_id, round) %>%
      summarise(
        detected_run_ts = max(to_run_ts, na.rm = TRUE),
        inferred_trade_events = n(),
        inferred_players_out = sum(players_out_n, na.rm = TRUE),
        inferred_players_in = sum(players_in_n, na.rm = TRUE),
        inferred_trade_pairs = list(bind_rows(inferred_trade_pairs)),
        .groups = "drop"
      ),
    by = c("user_team_id", "round")
  ) %>%
  left_join(
    actual_trade_history %>%
      group_by(user_team_id, round) %>%
      summarise(
    actual_trade_count = n(),
    actual_trades = list(tibble(
      buy_player_id = buy_player_id,
      sell_player_id = sell_player_id,
      trade_source = trade_source
    )),
    .groups = "drop"
  ),
    by = c("user_team_id", "round")
  ) %>%
  left_join(
    latest_team_round_stats %>%
      select(user_team_id, round, total_changes, trade_boosts_used),
    by = c("user_team_id", "round")
  ) %>%
  left_join(
    team_lookup %>% select(user_team_id, team_name, coach_name, is_me),
    by = "user_team_id"
  ) %>%
  mutate(
    behaviour_source = case_when(
      !map_lgl(actual_trades, is.null) ~ "actual_api_plus_snapshots",
      TRUE ~ "snapshot_inference_plus_team_stats"
    )
  )

league_ownership_movement <- player_catalog %>%
  transmute(
    run_ts = run_ts,
    player_id,
    full_name,
    ownership_percentage = NA_real_,
    ownership_movement = NA_real_
  )

captaincy_vc_table <- team_players_latest %>%
  group_by(user_team_id, round, player_id) %>%
  summarise(
    captain_flag = NA,
    vice_captain_flag = NA,
    captaincy_source = "unavailable_from_confirmed_sources",
    .groups = "drop"
  )

structure_health_table <- squad_round_enriched %>%
  group_by(user_team_id, team_name, coach_name, is_me, round) %>%
  summarise(
    players_in_squad = n_distinct(player_id),
    selected_players = sum(selected_this_week %in% TRUE, na.rm = TRUE),
    field_players = sum(field_bench_npr == "field", na.rm = TRUE),
    bench_players = sum(field_bench_npr == "bench", na.rm = TRUE),
    npr_players = sum(field_bench_npr == "npr", na.rm = TRUE),
    locked_players = sum(currently_locked %in% TRUE, na.rm = TRUE),
    dpp_players = sum(dpp_flexibility_usefulness > 0, na.rm = TRUE),
    avg_projected_score_this_week = if_else(
      all(is.na(projected_score_this_week)),
      NA_real_,
      mean(projected_score_this_week, na.rm = TRUE)
    ),
    .groups = "drop"
  )

scenario_refresh_table <- tibble(
  run_ts = run_ts,
  current_round = current_round,
  competition_status = competition_status,
  is_lockout = safe_lgl(settings$competition$is_lockout, FALSE),
  is_partial_lockout = safe_lgl(settings$competition$is_partial_lockout, FALSE),
  next_refresh_trigger = safe_chr(settings$competition$lockout_start),
  refresh_reason = "competition_lockout_window"
)

long_horizon_planning_table <- squad_round_enriched %>%
  filter(is_me %in% TRUE) %>%
  group_by(user_team_id, team_name, coach_name) %>%
  filter(round == max(round, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(user_team_id, team_name, coach_name) %>%
  summarise(
    run_ts = run_ts,
    current_round = current_round,
    current_squad_value = sum(current_price, na.rm = TRUE),
    projected_score_next_3_weeks = sum(projected_score_next_3_weeks, na.rm = TRUE),
    trades_remaining = game_rules_round_state$trades_remaining[[1]],
    boosts_remaining = game_rules_round_state$boosts_remaining[[1]],
    finals_round = game_rules_round_state$finals_round[[1]],
    next_bye_rounds = list(game_rules_round_state$bye_round_structure[[1]]),
    .groups = "drop"
  )
```

## 14. Build cash and team value by round

```{r}
starting_cap <- 11950000L

# Sum player prices to rebuild each squad's market value by round.
team_prices_by_round <- team_players_latest %>%
  distinct(user_team_id, round, player_id) %>%
  left_join(
    player_price_history_sc %>%
      select(player_id, round, price),
    by = c("player_id", "round")
  ) %>%
  group_by(user_team_id, round) %>%
  summarise(
    squad_size = n(),
    n_players_priced = sum(!is.na(price)),
    squad_value_calc = if_else(
      n_players_priced == squad_size,
      sum(price, na.rm = TRUE),
      NA_real_
    ),
    .groups = "drop"
  )

team_round_rosters <- team_players_latest %>%
  distinct(user_team_id, round, player_id)

min_round_available <- min(team_round_rosters$round, na.rm = TRUE)
max_round_available <- max(team_round_rosters$round, na.rm = TRUE)

# Identify players newly in a roster compared with the prior round.
team_ins <- team_round_rosters %>%
  filter(round > min_round_available) %>%
  anti_join(
    team_round_rosters %>%
      mutate(round = round + 1L),
    by = c("user_team_id", "round", "player_id")
  ) %>%
  rename(player_id_in = player_id)

# Identify players removed from a roster compared with the prior round.
team_outs <- team_round_rosters %>%
  filter(round < max_round_available) %>%
  mutate(round = round + 1L) %>%
  anti_join(
    team_round_rosters,
    by = c("user_team_id", "round", "player_id")
  ) %>%
  rename(player_id_out = player_id)

# Price trade events using the prior round's price point.
trade_events_priced <- team_ins %>%
  group_by(user_team_id, round) %>%
  mutate(trade_slot = row_number()) %>%
  ungroup() %>%
  full_join(
    team_outs %>%
      group_by(user_team_id, round) %>%
      mutate(trade_slot = row_number()) %>%
      ungroup(),
    by = c("user_team_id", "round", "trade_slot")
  ) %>%
  left_join(
    player_price_history_sc %>%
      transmute(
        player_id_in = player_id,
        round = round + 1L,
        buy_price = price
      ),
    by = c("player_id_in", "round")
  ) %>%
  left_join(
    player_price_history_sc %>%
      transmute(
        player_id_out = player_id,
        round = round + 1L,
        sell_price = price
      ),
    by = c("player_id_out", "round")
  ) %>%
  mutate(
    cash_delta = coalesce(sell_price, 0) - coalesce(buy_price, 0)
  )

trade_cash_by_round <- trade_events_priced %>%
  group_by(user_team_id, round) %>%
  summarise(
    trade_ins = sum(!is.na(player_id_in)),
    trade_outs = sum(!is.na(player_id_out)),
    total_buy_price = sum(coalesce(buy_price, 0), na.rm = TRUE),
    total_sell_price = sum(coalesce(sell_price, 0), na.rm = TRUE),
    cash_delta = sum(cash_delta, na.rm = TRUE),
    .groups = "drop"
  )

initial_cash_by_team <- team_prices_by_round %>%
  group_by(user_team_id) %>%
  slice_min(round, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  transmute(
    user_team_id,
    initial_squad_value_calc = squad_value_calc,
    initial_cash_calc = starting_cap - squad_value_calc
  )

cash_by_round <- team_prices_by_round %>%
  left_join(trade_cash_by_round, by = c("user_team_id", "round")) %>%
  left_join(initial_cash_by_team, by = "user_team_id") %>%
  arrange(user_team_id, round) %>%
  group_by(user_team_id) %>%
  mutate(
    trade_ins = coalesce(trade_ins, 0L),
    trade_outs = coalesce(trade_outs, 0L),
    total_buy_price = coalesce(total_buy_price, 0),
    total_sell_price = coalesce(total_sell_price, 0),
    cash_delta = coalesce(cash_delta, 0),
    cash_end_round_calc = initial_cash_calc + cumsum(cash_delta),
    team_value_total_calc = squad_value_calc + cash_end_round_calc
  ) %>%
  ungroup()

negative_cash_check <- cash_by_round %>%
  filter(cash_end_round_calc < 0)

if (nrow(negative_cash_check) > 0) {
  print_results(negative_cash_check)
  stop("Stopping: negative cash balances remain after applying previous-round trade pricing")
}
```

## 15. Attach value fields back to ladder history safely and save outputs

```{r}
ladder_value_compare <- ladder_history %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(user_team_id, round, squad_value) %>%
  left_join(
    cash_by_round %>%
      select(
        user_team_id,
        round,
        squad_size,
        n_players_priced,
        squad_value_calc,
        initial_cash_calc,
        trade_ins,
        trade_outs,
        total_buy_price,
        total_sell_price,
        cash_delta,
        cash_end_round_calc,
        team_value_total_calc
      ),
    by = c("user_team_id", "round")
  ) %>%
  mutate(
    squad_value_diff = squad_value_calc - squad_value
  )

ladder_history <- ladder_history %>%
  select(
    -any_of(c(
      "squad_size",
      "n_players_priced",
      "squad_value_calc",
      "initial_cash_calc",
      "trade_ins",
      "trade_outs",
      "total_buy_price",
      "total_sell_price",
      "cash_delta",
      "cash_end_round_calc",
      "team_value_total_calc",
      "squad_value_diff"
    ))
  ) %>%
  left_join(
    ladder_value_compare %>%
      select(
        user_team_id,
        round,
        squad_size,
        n_players_priced,
        squad_value_calc,
        initial_cash_calc,
        trade_ins,
        trade_outs,
        total_buy_price,
        total_sell_price,
        cash_delta,
        cash_end_round_calc,
        team_value_total_calc,
        squad_value_diff
      ),
    by = c("user_team_id", "round")
  )

checklist_coverage_status <- tibble(
  checklist_item = c(
    "game_rules_round_state",
    "master_player_table",
    "player_scoring_component_history",
    "team_list_role_certainty",
    "fixture_matchup_table",
    "team_performance_context",
    "cash_generation_model",
    "your_squad_table",
    "opponent_behaviour_history",
    "league_ownership_movement",
    "availability_risk_table",
    "captaincy_vc_table",
    "trade_candidate_comparison_table",
    "structure_health_table",
    "scenario_table",
    "long_horizon_planning_table"
  ),
  table_name = c(
    "game_rules_round_state",
    "master_player_round_latest",
    "player_scoring_component_history",
    "team_list_role_certainty",
    "fixture_matchup_table",
    "team_performance_context",
    "cash_generation_model",
    "squad_round_enriched",
    "opponent_behaviour_history",
    "league_ownership_movement",
    "availability_risk_table",
    "captaincy_vc_table",
    "trade_candidate_comparison_table",
    "structure_health_table",
    "scenario_refresh_table",
    "long_horizon_planning_table"
  ),
  row_count = c(
    nrow(game_rules_round_state),
    nrow(master_player_round_latest),
    nrow(player_scoring_component_history),
    nrow(team_list_role_certainty),
    nrow(fixture_matchup_table),
    nrow(team_performance_context),
    nrow(cash_generation_model),
    nrow(squad_round_enriched),
    nrow(opponent_behaviour_history),
    nrow(league_ownership_movement),
    nrow(availability_risk_table),
    nrow(captaincy_vc_table),
    0L,
    nrow(structure_health_table),
    nrow(scenario_refresh_table),
    nrow(long_horizon_planning_table)
  ),
  status = c(
    "partial",
    "partial",
    "partial",
    "partial",
    "unavailable",
    "unavailable",
    "partial",
    "partial",
    "partial",
    "unavailable",
    "partial",
    "unavailable",
    "unavailable",
    "partial",
    "partial",
    "partial"
  ),
  source_endpoint = c(
    "/settings, /players-cf, /userteams/{id}/statsPlayers",
    "/players-cf, initialvalue.php, data-yearplot.php",
    "data-yearplot.php",
    "/userteams/{id}/statsPlayers, data-yearplot.php",
    "Unavailable from confirmed sources",
    "Unavailable from confirmed sources",
    "initialvalue.php, data-yearplot.php",
    "/userteams/{id}/statsPlayers, /players-cf, data-yearplot.php",
    "/userteams/{id}/statsPlayers, ladderAndFixtures",
    "Unavailable from confirmed sources",
    "/players-cf",
    "Unavailable from confirmed sources",
    "Unavailable from confirmed sources",
    "/userteams/{id}/statsPlayers, /players-cf",
    "/settings",
    "/settings, /userteams/{id}/statsPlayers"
  ),
  notes = c(
    "Confirmed competition rules, lockout window, squad limits, bye rounds, and player lock state via list columns; Origin-specific rounds remain unavailable.",
    "Current price, status, team, DPP, history lists, and recent averages are confirmed; breakeven, ownership, role, goal-kicking, and return timeline remain unavailable.",
    "Confirmed score, minutes, price-derived volatility, floor, ceiling, and PPM; base-stat components are unavailable from confirmed sources.",
    "Confirmed squad selection order and recent minutes for league rosters; global NRL team lists, role threats, and late omission probabilities remain unavailable.",
    "No confirmed NRL fixture endpoint with venue/rest/matchup fields was identified in the validated source set.",
    "No confirmed NRL team performance endpoint with tries, linebreaks, possession, or defensive splits was identified in the validated source set.",
    "Confirmed starting/current price, recent price movement, projected next price, and cash classification; breakeven trend and peak-cash timing remain unavailable.",
    "Confirmed acquisition timing, prices, lock state, selection slot, and simple projections; next-3-week value movement and bye utility remain approximate or unavailable.",
    "Confirmed full squad history, cumulative change counts, and boost usage by team-round; exact opponent ins/outs are only inferred from snapshots unless exposed for the authenticated team.",
    "Ownership percentage and movement were not present in the confirmed source set.",
    "Confirmed current active, injury/suspension, and lock indicators from /players-cf; expected return dates remain unavailable.",
    "Captain and vice-captain selections were not present in the confirmed source set.",
    "Trade comparison scenarios are not available from confirmed sources and were not fabricated.",
    "Confirmed structural metrics from squad composition and lock state; bye resilience remains limited without a confirmed NRL fixture source.",
    "Confirmed competition refresh trigger from /settings lockout window; per-game rolling refresh triggers remain unavailable without a confirmed NRL fixture feed.",
    "Confirmed long-horizon summary uses current squad value, trades, boosts, and bye rounds; deeper future projection fields remain partial."
  )
)

saveRDS(ladder_history, path_ladder_history)
saveRDS(fixture_triggers, path_fixture_triggers)
saveRDS(master_player_round_latest, path_master_player_round_latest)
saveRDS(opponent_behaviour_history, path_opponent_behaviour_history)
saveRDS(squad_round_enriched, path_squad_round_enriched)
saveRDS(game_rules_round_state, path_game_rules_round_state)
saveRDS(player_scoring_component_history, path_player_scoring_component_history)
saveRDS(team_list_role_certainty, path_team_list_role_certainty)
saveRDS(fixture_matchup_table, path_fixture_matchup_table)
saveRDS(team_performance_context, path_team_performance_context)
saveRDS(cash_generation_model, path_cash_generation_model)
saveRDS(league_ownership_movement, path_league_ownership_movement)
saveRDS(availability_risk_table, path_availability_risk_table)
saveRDS(captaincy_vc_table, path_captaincy_vc_table)
saveRDS(structure_health_table, path_structure_health_table)
saveRDS(scenario_refresh_table, path_scenario_refresh_table)
saveRDS(long_horizon_planning_table, path_long_horizon_planning_table)
saveRDS(checklist_coverage_status, path_checklist_coverage_status)
```

## 16. Validation summary

```{r}
major_tables <- list(
  game_rules_round_state = game_rules_round_state,
  master_player_round_latest = master_player_round_latest,
  player_scoring_component_history = player_scoring_component_history,
  team_list_role_certainty = team_list_role_certainty,
  fixture_matchup_table = fixture_matchup_table,
  team_performance_context = team_performance_context,
  cash_generation_model = cash_generation_model,
  squad_round_enriched = squad_round_enriched,
  opponent_behaviour_history = opponent_behaviour_history,
  availability_risk_table = availability_risk_table,
  structure_health_table = structure_health_table,
  long_horizon_planning_table = long_horizon_planning_table
)

row_count_summary <- tibble(
  table_name = names(major_tables),
  row_count = map_int(major_tables, nrow)
)

unresolved_gaps <- checklist_coverage_status %>%
  filter(status != "implemented")

sample_rows <- purrr::imap(
  major_tables,
  ~ if (nrow(.x) == 0) NULL else utils::head(.x, 1)
)

row_count_summary
unresolved_gaps %>% select(checklist_item, status, notes)
sample_rows
```

## 17. Final returned objects

```{r}
list(
  current_round = current_round,
  rounds_pulled = rounds_to_pull,
  ladder_history = ladder_history,
  fixtures_history = fixtures_history,
  team_players_latest = team_players_latest,
  team_round_stats_history = team_round_stats_history,
  actual_trade_history = actual_trade_history,
  inferred_changes = inferred_changes,
  grog_baguettes_latest = grog_baguettes_latest,
  grog_baguettes_changes = grog_baguettes_changes,
  league_change_summary = league_change_summary,
  run_log = run_log,
  team_round_results = team_round_results,
  player_price_history_sc = player_price_history_sc,
  master_player_round_latest = master_player_round_latest,
  player_scoring_component_history = player_scoring_component_history,
  team_list_role_certainty = team_list_role_certainty,
  cash_generation_model = cash_generation_model,
  squad_round_enriched = squad_round_enriched,
  opponent_behaviour_history = opponent_behaviour_history,
  cash_by_round = cash_by_round,
  ladder_value_compare = ladder_value_compare,
  fixture_triggers = fixture_triggers,
  game_rules_round_state = game_rules_round_state,
  fixture_matchup_table = fixture_matchup_table,
  team_performance_context = team_performance_context,
  availability_risk_table = availability_risk_table,
  structure_health_table = structure_health_table,
  scenario_refresh_table = scenario_refresh_table,
  long_horizon_planning_table = long_horizon_planning_table,
  checklist_coverage_status = checklist_coverage_status
)
```
