---
title: "Ingest local league data and tracking"
output: html_document
---

## Purpose

This Rmd pulls authenticated SuperCoach league data, stores historical snapshots safely across reruns, rebuilds the latest known team state, and calculates round-by-round cash balances.

## Outputs

This script writes the following `.rds` files under the league-specific data folder:

- `ladder_history.rds`
- `team_players_snapshots.rds`
- `team_players_latest.rds`
- `team_round_signatures.rds`
- `inferred_changes.rds`
- `run_log.rds`
- `player_price_history_2026.rds`
- `players_cf_2026.rds`
- `player_id_lookup.rds`
- `player_price_history_sc.rds`

## Notes on reruns, table grain and querying

### Core design

This script is designed to be rerun throughout the season, including multiple times within the same live round.

It uses an append-history pattern for some tables and a latest-state pattern for others.

The key distinction is:

- history tables preserve reruns and should be queried with `run_ts` awareness
- latest tables collapse history down to the most recent known state at the relevant grain

### Table grain and intended use

#### `ladder_history`
This is a history table.

Grain:
- one row per `user_team_id`, `round`, `run_ts`

Behaviour:
- appends on every rerun for the pulled rounds
- duplicate `user_team_id + round` combinations across reruns are expected
- this is not corruption; it is how rerun history is preserved

Use this table when you want:
- ladder snapshot history
- to compare how ladder fields changed across reruns
- to inspect what was known at a given run timestamp

Do not query this table directly if you want one current row per team per round.

For latest-only ladder queries, first collapse to the most recent `run_ts` per `user_team_id + round`.

#### `team_players_snapshots`
This is a snapshot history table.

Grain:
- one row per player within a stored team-round snapshot, identified by `run_ts`

Behaviour:
- only appends when a team-round roster signature changed
- repeated reruns with no roster change do not append duplicate snapshots
- preserves roster state history for changed team-rounds over time

Use this table when you want:
- roster history
- to inspect how a team changed during a live round
- to reconstruct prior membership for inferred changes

#### `team_round_signatures`
This is the team-round snapshot index.

Grain:
- one row per stored team-round snapshot

Behaviour:
- one row per `user_team_id + round + run_ts` when a new signature is detected
- used to determine whether a rerun produced a genuinely new roster state

Use this table when you want:
- a compact history of detected roster states
- the latest available snapshot timestamp for each team-round

#### `team_players_latest`
This is the latest-state roster table.

Grain:
- one row per player for the latest known snapshot of each `user_team_id + round`

Behaviour:
- rebuilt from snapshot history after each run
- already deduplicated to the latest `run_ts` per `user_team_id + round`

Use this table when you want:
- current known roster state by round
- round-to-round roster comparisons
- downstream joins that should not duplicate across reruns

#### `inferred_changes`
This is a change-history table.

Grain:
- one row per detected roster-state change for a `user_team_id + round`

Behaviour:
- appends only when a new snapshot differs from the previous stored snapshot
- compares prior stored membership to current stored membership
- reflects observed net state changes between snapshots, not every transient move a coach may have made and reversed between runs

Use this table when you want:
- inferred ins and outs between observed snapshots
- live-round monitoring of opponent net changes

#### `cash_by_round`
This is a latest-state team-round table.

Grain:
- one row per `user_team_id + round`

Behaviour:
- rebuilt from `team_players_latest`
- does not preserve rerun history itself
- intended for one current cash/value result per team-round

Use this table when you want:
- current reconstructed cash by round
- team-round value outputs without rerun duplication

### Querying rules

#### When to use history tables
Use `ladder_history`, `team_players_snapshots`, `team_round_signatures`, and `inferred_changes` when you care about:
- rerun history
- intra-round monitoring
- auditability
- comparing what changed between runs

#### When to use latest-state tables
Use `team_players_latest`, `cash_by_round`, and a latest-collapsed ladder view when you want:
- one current row per business key
- outputs for reporting
- joins that should not multiply because of reruns


## 1. Setup

```{r}
suppressPackageStartupMessages({
  rm(list = ls())
  gc()
  library(pai)
  load_pacakges()
  load_pacakges_fap()
})

library(ggrepel)
library(httr2)
library(jsonlite)
library(dplyr)
library(tibble)
library(purrr)
library(tidyr)
library(furrr)
library(stringr)

source("functions.R")
```

## 2. Configuration

```{r}
league_id <- 21064
season_rounds <- 1:27
base_url <- "https://www.supercoach.com.au/2026/api/nrl/classic/v1"
run_ts <- Sys.time()

Sys.setenv(
  SC_BEARER = "6a21e2da868f50ebb0fe96dff87b4a02b191fbe9"
)

data_dir <- file.path("data", paste0("supercoach_league_", league_id))
dir.create(data_dir, recursive = TRUE, showWarnings = FALSE)

path_ladder_history <- file.path(data_dir, "ladder_history.rds")
path_team_players_snapshots <- file.path(data_dir, "team_players_snapshots.rds")
path_team_players_latest <- file.path(data_dir, "team_players_latest.rds")
path_team_round_signatures <- file.path(data_dir, "team_round_signatures.rds")
path_inferred_changes <- file.path(data_dir, "inferred_changes.rds")
path_run_log <- file.path(data_dir, "run_log.rds")
path_player_price_history_2026 <- file.path(data_dir, "player_price_history_2026.rds")
path_players_cf_2026 <- file.path(data_dir, "players_cf_2026.rds")
path_player_id_lookup <- file.path(data_dir, "player_id_lookup.rds")
path_player_price_history_sc <- file.path(data_dir, "player_price_history_sc.rds")
```

## 3. Helper functions

```{r}
normalise_player_name <- function(x) {
  x %>%
    stringr::str_to_lower() %>%
    stringr::str_replace_all("\\*+", " ") %>%
    stringr::str_replace_all("[`´‘’']", "") %>%
    stringr::str_replace_all("[^a-z0-9, ]", " ") %>%
    stringr::str_squish() %>%
    stringr::str_replace_all(" ", "")
}

`%||%` <- function(a, b) if (is.null(a)) b else a

read_rds_if_exists <- function(path, default) {
  if (file.exists(path)) readRDS(path) else default
}

coalesce_chr <- function(x) {
  x <- as.character(x)
  x[is.na(x)] <- ""
  x
}

sc_get <- function(path, query = list()) {
  request(paste0(base_url, path)) %>%
    req_headers(
      Accept = "application/json",
      Authorization = paste("Bearer", Sys.getenv("SC_BEARER")),
      Referer = paste0(
        "https://www.supercoach.com.au/nrl/classic/leagues(popup:leagues/",
        league_id,
        "/head-2-head)"
      ),
      Origin = "https://www.supercoach.com.au",
      `User-Agent` = "Mozilla/5.0"
    ) %>%
    req_url_query(!!!query) %>%
    req_perform() %>%
    resp_body_string()
}

pluck_chr1 <- function(x, ...) {
  out <- purrr::pluck(x, ..., .default = NA_character_)
  if (length(out) == 0 || is.null(out)) NA_character_ else as.character(out[[1]])
}

pluck_num1 <- function(x, ...) {
  out <- purrr::pluck(x, ..., .default = NA_real_)
  if (length(out) == 0 || is.null(out)) NA_real_ else as.numeric(out[[1]])
}

get_ladder_fixtures_round <- function(round) {
  txt <- sc_get(
    paste0("/leagues/", league_id, "/ladderAndFixtures"),
    query = list(round = round)
  )

  x <- fromJSON(txt, simplifyVector = FALSE)

  ladder_tbl <- if (is.null(x$ladder) || length(x$ladder) == 0) {
    tibble()
  } else {
    map_dfr(x$ladder, function(z) {
      tibble(
        run_ts = run_ts,
        league_id = z$league_id %||% league_id,
        round = z$round %||% round,
        user_team_id = as.integer(z$user_team_id %||% NA_integer_),
        team_name = pluck_chr1(z, "userTeam", "teamname"),
        coach_name = pluck_chr1(z, "userTeam", "user", "first_name"),
        is_me = purrr::pluck(z, "userTeam", "user", "is_me", .default = NA),
        wins = z$wins %||% NA_real_,
        losses = z$losses %||% NA_real_,
        draws = z$draws %||% NA_real_,
        ladder_points = z$points %||% NA_real_,
        points_for = z$points_for %||% NA_real_,
        points_against = z$points_against %||% NA_real_,
        position = z$position %||% NA_real_,
        last_position = z$last_position %||% NA_real_,
        wins_last5 = z$wins_last5 %||% NA_real_,
        losses_last5 = z$losses_last5 %||% NA_real_,
        draws_last5 = z$draws_last5 %||% NA_real_,
        round_points = pluck_num1(z, "userTeam", "stats", 1, "points"),
        total_points = pluck_num1(z, "userTeam", "stats", 1, "total_points"),
        overall_position = pluck_num1(z, "userTeam", "stats", 1, "position"),
        round_position = pluck_num1(z, "userTeam", "stats", 1, "round_position"),
        squad_value = pluck_num1(z, "userTeam", "stats", 1, "price"),
        price_change = pluck_num1(z, "userTeam", "stats", 1, "price_change"),
        total_price_change = pluck_num1(z, "userTeam", "stats", 1, "total_price_change"),
        rounds_played = pluck_num1(z, "userTeam", "stats", 1, "rounds_played")
      )
    })
  }

  fixtures_tbl <- if (is.null(x$fixtures) || length(x$fixtures) == 0) {
    tibble()
  } else {
    tibble(
      run_ts = run_ts,
      league_id = league_id,
      round = round,
      raw = I(list(x$fixtures))
    )
  }

  list(
    ladder = ladder_tbl,
    fixtures = fixtures_tbl,
    raw_json = txt
  )
}

get_stats_players_round <- function(team_id, round) {
  txt <- sc_get(
    paste0("/userteams/", team_id, "/statsPlayers"),
    query = list(round = round)
  )

  x <- fromJSON(txt, simplifyVector = FALSE)
  top_name <- intersect(names(x), c("players", "statsPlayers", "data"))

  players_tbl <- if (length(top_name) == 0 || is.null(x[[top_name[1]]]) || length(x[[top_name[1]]]) == 0) {
    tibble(
      run_ts = run_ts,
      user_team_id = as.integer(team_id),
      round = as.integer(round)
    )
  } else {
    bind_rows(x[[top_name[1]]]) %>%
      as_tibble() %>%
      mutate(
        run_ts = run_ts,
        user_team_id = as.integer(team_id),
        round = as.integer(round)
      )
  }

  list(
    players = players_tbl,
    raw_json = txt
  )
}

detect_current_round <- function(rounds = season_rounds) {
  seed_ladder <- tryCatch(
    get_ladder_fixtures_round(1)$ladder,
    error = function(e) tibble()
  )

  seed_team_id <- seed_ladder %>%
    filter(!is.na(user_team_id)) %>%
    distinct(user_team_id) %>%
    pull(user_team_id) %>%
    first()

  if (length(seed_team_id) == 0 || is.na(seed_team_id)) {
    stop("Could not find a valid seed team ID from round 1 ladder")
  }

  for (r in rev(rounds)) {
    player_tbl <- tryCatch(
      {
        out <- get_stats_players_round(seed_team_id, r)$players
        if (!is.data.frame(out)) tibble() else out
      },
      error = function(e) tibble()
    )

    if (
      nrow(player_tbl) > 0 &&
      "round" %in% names(player_tbl) &&
      any(player_tbl$round == r, na.rm = TRUE)
    ) {
      return(as.integer(r))
    }
  }

  stop("Could not detect current round from statsPlayers")
}

build_roster_signature <- function(df) {
  if (nrow(df) == 0 || !"player_id" %in% names(df)) return(NA_character_)

  df %>%
    transmute(
      sig = paste(
        coalesce_chr(player_id),
        coalesce_chr(position),
        coalesce_chr(position_long),
        coalesce_chr(position_sort),
        coalesce_chr(picked),
        sep = "::"
      )
    ) %>%
    arrange(sig) %>%
    pull(sig) %>%
    paste(collapse = "|")
}

extract_roster_membership <- function(df) {
  if (nrow(df) == 0 || !"player_id" %in% names(df)) {
    return(tibble(player_id = integer()))
  }

  df %>%
    filter(!is.na(player_id)) %>%
    distinct(player_id) %>%
    arrange(player_id)
}

pair_inferred_trades <- function(players_out, players_in) {
  n_out <- length(players_out)
  n_in <- length(players_in)
  n_pair <- min(n_out, n_in)

  tibble(
    trade_seq = seq_len(n_pair),
    player_out_id = if (n_pair > 0) players_out[seq_len(n_pair)] else integer(),
    player_in_id = if (n_pair > 0) players_in[seq_len(n_pair)] else integer()
  )
}


```

## 4. Empty table templates

```{r}
empty_ladder_history <- tibble(
  run_ts = as.POSIXct(character()),
  league_id = integer(),
  round = integer(),
  user_team_id = integer(),
  team_name = character(),
  coach_name = character(),
  is_me = logical(),
  wins = numeric(),
  losses = numeric(),
  draws = numeric(),
  ladder_points = numeric(),
  points_for = numeric(),
  points_against = numeric(),
  position = numeric(),
  last_position = numeric(),
  wins_last5 = numeric(),
  losses_last5 = numeric(),
  draws_last5 = numeric(),
  round_points = numeric(),
  total_points = numeric(),
  overall_position = numeric(),
  round_position = numeric(),
  squad_value = numeric(),
  price_change = numeric(),
  total_price_change = numeric(),
  rounds_played = numeric()
)

empty_team_players_snapshots <- tibble(
  run_ts = as.POSIXct(character()),
  user_team_id = integer(),
  round = integer()
)

empty_team_players_latest <- tibble(
  run_ts = as.POSIXct(character()),
  user_team_id = integer(),
  round = integer()
)

empty_team_round_signatures <- tibble(
  run_ts = as.POSIXct(character()),
  league_id = integer(),
  user_team_id = integer(),
  round = integer(),
  roster_signature = character()
)

empty_inferred_changes <- tibble(
  detected_run_ts = as.POSIXct(character()),
  from_run_ts = as.POSIXct(character()),
  to_run_ts = as.POSIXct(character()),
  league_id = integer(),
  user_team_id = integer(),
  round = integer(),
  players_out = list(),
  players_in = list(),
  players_out_n = integer(),
  players_in_n = integer(),
  inferred_trade_pairs = list()
)

empty_run_log <- tibble(
  run_ts = as.POSIXct(character()),
  league_id = integer(),
  first_run = logical(),
  current_round = integer(),
  rounds_pulled = character(),
  ladder_rows_new = integer(),
  player_snapshot_rows_new = integer(),
  changed_team_rounds = integer(),
  failed_team_rounds = integer()
)
```

## 5. Load existing history

```{r}
ladder_history_existing <- read_rds_if_exists(path_ladder_history, empty_ladder_history)
team_players_snapshots_existing <- read_rds_if_exists(path_team_players_snapshots, empty_team_players_snapshots)
team_players_latest_existing <- read_rds_if_exists(path_team_players_latest, empty_team_players_latest)
team_round_signatures_existing <- read_rds_if_exists(path_team_round_signatures, empty_team_round_signatures)
inferred_changes_existing <- read_rds_if_exists(path_inferred_changes, empty_inferred_changes)
run_log_existing <- read_rds_if_exists(path_run_log, empty_run_log)
```

## 6. Detect current round

```{r}
first_run <- nrow(ladder_history_existing) == 0 || nrow(team_round_signatures_existing) == 0
current_round <- detect_current_round(season_rounds)
```

## 7. Pull ladder and team-round data

```{r}
rounds_to_pull <- if (first_run) {
  seq_len(current_round)
} else {
  current_round
}

# Pull ladder data for the required rounds.
ladder_pulls <- map(rounds_to_pull, get_ladder_fixtures_round)
ladder_history_new <- map_dfr(ladder_pulls, "ladder")

ladder_history <- bind_rows(
  ladder_history_existing,
  ladder_history_new
) %>%
  arrange(run_ts, round, position, user_team_id)

team_lookup <- ladder_history %>%
  distinct(user_team_id, team_name, coach_name, is_me) %>%
  filter(!is.na(user_team_id))

team_round_grid <- ladder_history_new %>%
  distinct(user_team_id, round) %>%
  filter(!is.na(user_team_id), !is.na(round)) %>%
  arrange(round, user_team_id)

future::plan(multisession, workers = max(1, future::availableCores() - 1))

# Pull team player lists for each team-round in the new ladder pull.
team_players_pull <- team_round_grid %>%
  mutate(
    pull = future_pmap(
      list(user_team_id, round),
      ~ tryCatch(
        get_stats_players_round(..1, ..2),
        error = function(e) list(players = tibble(), raw_json = NA_character_, error = conditionMessage(e))
      ),
      .options = furrr_options(seed = TRUE)
    ),
    players = map(pull, "players"),
    pull_error = map_chr(pull, ~ .x$error %||% NA_character_),
    pull_ok = map_lgl(pull, ~ is.null(.x$error)),
    player_rows = map_int(players, nrow)
  )
```

## 8. Build snapshot signatures and protect reruns

```{r}
latest_existing_signatures <- team_round_signatures_existing %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(user_team_id, round, prev_run_ts = run_ts, prev_roster_signature = roster_signature)

# Only compare signatures when the new pull succeeded and contains a roster shape we trust.
team_round_results <- team_players_pull %>%
  mutate(
    players_core = map(players, ~ .x %>% select(-any_of("raw_json"))),
    roster_signature = map_chr(players_core, build_roster_signature)
  ) %>%
  left_join(
    latest_existing_signatures,
    by = c("user_team_id", "round")
  ) %>%
  mutate(
    is_valid_roster_pull = pull_ok & !is.na(roster_signature) & player_rows > 0,
    is_new_snapshot = case_when(
      !is_valid_roster_pull ~ FALSE,
      is.na(prev_roster_signature) ~ TRUE,
      roster_signature != prev_roster_signature ~ TRUE,
      TRUE ~ FALSE
    )
  )

team_round_signatures_new <- team_round_results %>%
  filter(is_new_snapshot) %>%
  transmute(
    run_ts = run_ts,
    league_id = league_id,
    user_team_id,
    round,
    roster_signature
  )
```

## 9. Append snapshots and rebuild latest team state

```{r}
team_players_snapshots_new <- team_round_results %>%
  filter(is_new_snapshot) %>%
  select(players_core) %>%
  unnest(players_core)

team_round_signatures <- bind_rows(
  team_round_signatures_existing,
  team_round_signatures_new
) %>%
  arrange(run_ts, round, user_team_id)

team_players_snapshots <- bind_rows(
  team_players_snapshots_existing,
  team_players_snapshots_new
) %>%
  arrange(run_ts, round, user_team_id)

latest_snapshot_per_team_round <- team_round_signatures %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(user_team_id, round, latest_run_ts = run_ts)

team_players_latest <- team_players_snapshots %>%
  inner_join(
    latest_snapshot_per_team_round,
    by = c("user_team_id", "round")
  ) %>%
  filter(run_ts == latest_run_ts) %>%
  select(-latest_run_ts) %>%
  arrange(user_team_id, round, position_sort, position, player_id)
```

## 10. Infer roster changes between snapshots

```{r}
previous_membership_lookup <- team_round_signatures_existing %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(user_team_id, round, prev_run_ts = run_ts)

previous_membership <- previous_membership_lookup %>%
  inner_join(
    team_players_snapshots_existing,
    by = c("user_team_id", "round", "prev_run_ts" = "run_ts")
  ) %>%
  group_by(user_team_id, round, prev_run_ts) %>%
  summarise(
    prev_players = list(extract_roster_membership(pick(everything()))),
    .groups = "drop"
  )

current_membership <- team_round_results %>%
  filter(is_new_snapshot) %>%
  transmute(
    user_team_id,
    round,
    detected_run_ts = run_ts,
    from_run_ts = prev_run_ts,
    to_run_ts = run_ts,
    current_players = map(players_core, extract_roster_membership)
  )

inferred_changes_new <- current_membership %>%
  left_join(previous_membership, by = c("user_team_id", "round", "from_run_ts" = "prev_run_ts")) %>%
  mutate(
    prev_players = map(prev_players, ~ if (is.null(.x)) tibble(player_id = integer()) else .x),
    players_in_tbl = map2(current_players, prev_players, ~ anti_join(.x, .y, by = "player_id")),
    players_out_tbl = map2(prev_players, current_players, ~ anti_join(.x, .y, by = "player_id")),
    players_in = map(players_in_tbl, ~ .x$player_id),
    players_out = map(players_out_tbl, ~ .x$player_id),
    players_in_n = map_int(players_in, length),
    players_out_n = map_int(players_out, length),
    inferred_trade_pairs = map2(players_out, players_in, pair_inferred_trades)
  ) %>%
  transmute(
    detected_run_ts,
    from_run_ts,
    to_run_ts,
    league_id = league_id,
    user_team_id,
    round,
    players_out,
    players_in,
    players_out_n,
    players_in_n,
    inferred_trade_pairs
  )

inferred_changes <- bind_rows(
  inferred_changes_existing,
  inferred_changes_new
) %>%
  arrange(to_run_ts, round, user_team_id)
```

## 11. Save league outputs and run log

```{r}
run_log <- bind_rows(
  run_log_existing,
  tibble(
    run_ts = run_ts,
    league_id = league_id,
    first_run = first_run,
    current_round = current_round,
    rounds_pulled = paste(rounds_to_pull, collapse = ","),
    ladder_rows_new = nrow(ladder_history_new),
    player_snapshot_rows_new = nrow(team_players_snapshots_new),
    changed_team_rounds = nrow(team_round_signatures_new),
    failed_team_rounds = sum(!team_round_results$pull_ok)
  )
)

saveRDS(ladder_history, path_ladder_history)
saveRDS(team_players_snapshots, path_team_players_snapshots)
saveRDS(team_players_latest, path_team_players_latest)
saveRDS(team_round_signatures, path_team_round_signatures)
saveRDS(inferred_changes, path_inferred_changes)
saveRDS(run_log, path_run_log)

grog_baguettes_team_id <- team_lookup %>%
  filter(is_me %in% TRUE) %>%
  distinct(user_team_id) %>%
  pull(user_team_id) %>%
  first()

grog_baguettes_latest <- team_players_latest %>%
  filter(user_team_id == grog_baguettes_team_id)

grog_baguettes_changes <- inferred_changes %>%
  filter(user_team_id == grog_baguettes_team_id) %>%
  arrange(desc(to_run_ts))

league_change_summary <- inferred_changes %>%
  left_join(
    team_lookup %>% distinct(user_team_id, team_name, coach_name),
    by = "user_team_id"
  ) %>%
  arrange(desc(to_run_ts), round, team_name)
```

## 12. Pull player master data

```{r}
get_players_cf <- function(embed = NULL, round = NULL) {
  req <- request(paste0(base_url, "/players-cf")) %>%
    req_headers(
      Accept = "application/json",
      Authorization = paste("Bearer", Sys.getenv("SC_BEARER")),
      Referer = paste0(
        "https://www.supercoach.com.au/nrl/classic/leagues(popup:leagues/",
        league_id,
        "/head-2-head)"
      ),
      Origin = "https://www.supercoach.com.au",
      `User-Agent` = "Mozilla/5.0"
    )

  query <- list()

  if (!is.null(embed)) {
    query$embed <- embed
  }

  if (!is.null(round)) {
    query$round <- round
  }

  req %>%
    req_url_query(!!!query) %>%
    req_perform() %>%
    resp_body_string() %>%
    fromJSON(simplifyDataFrame = TRUE) %>%
    as_tibble()
}

players_cf_2026 <- get_players_cf()

player_id_lookup <- players_cf_2026 %>%
  transmute(
    player_id = as.integer(id),
    player_name = paste(last_name, first_name, sep = ", ")
  ) %>%
  filter(!is.na(player_id), !is.na(player_name), player_name != "") %>%
  distinct(player_id, player_name) %>%
  arrange(player_id)
```

## 13. Pull external player price history

```{r}
get_initialvalue_players <- function(year = 2026) {
  request("https://www.nrlsupercoachstats.com/initialvalue.php") %>%
    req_user_agent("Mozilla/5.0") %>%
    req_url_query(
      year = year,
      grid_id = "list1",
      jqgrid_page = 1,
      rows = 2000,
      search = "false",
      nd = as.integer(Sys.time())
    ) %>%
    req_perform() %>%
    resp_body_string() %>%
    fromJSON(simplifyDataFrame = TRUE) %>%
    {\(.) as_tibble(.$rows)}() %>%
    transmute(
      player_name = Name %>%
        gsub("^.*?>", "", .) %>%
        gsub("</a>$", "", .)
    ) %>%
    distinct(player_name) %>%
    arrange(player_name)
}

get_yearplot_player <- function(player, year = 2026) {
  request("https://www.nrlsupercoachstats.com/highcharts/data-yearplot.php") %>%
    req_user_agent("Mozilla/5.0") %>%
    req_url_query(
      dropdown1 = player,
      YEAR = year
    ) %>%
    req_perform() %>%
    resp_body_string() %>%
    fromJSON(simplifyDataFrame = FALSE)
}

yearplot_to_tibble_year <- function(x, player, year = 2026) {
  rounds <- as.integer(unlist(x[[1]]$data))
  target_prefix <- as.character(year)

  out <- tibble(
    player_name = player,
    year = year,
    round = rounds
  )

  for (i in seq_along(x)[-1]) {
    nm <- x[[i]]$name %||% ""

    if (startsWith(nm, target_prefix)) {
      vals <- unlist(x[[i]]$data)
      clean_nm <- nm %>%
        str_remove(paste0("^", target_prefix)) %>%
        str_to_lower()

      out[[clean_nm]] <- vals
    }
  }

  out
}

safe_get_price_history <- function(player, year = 2026) {
  tryCatch(
    {
      get_yearplot_player(player, year) %>%
        yearplot_to_tibble_year(player = player, year = year)
    },
    error = function(e) {
      tibble(
        player_name = player,
        year = year,
        round = integer(),
        score = numeric(),
        mins = numeric(),
        price = numeric()
      )
    }
  )
}

year_to_pull <- 2026

player_lookup_2026 <- get_initialvalue_players(year_to_pull)

player_price_history_2026 <- map_dfr(
  player_lookup_2026$player_name,
  safe_get_price_history,
  year = year_to_pull
) %>%
  arrange(player_name, round)
```

## 14. Match external prices back to SuperCoach player ids

```{r}
player_id_lookup_norm <- player_id_lookup %>%
  mutate(player_name_norm = normalise_player_name(player_name))

player_price_history_2026_norm <- player_price_history_2026 %>%
  mutate(player_name_norm = normalise_player_name(player_name))

league_player_ids <- team_players_latest %>%
  distinct(player_id)

player_id_lookup_norm_scoped <- player_id_lookup_norm %>%
  semi_join(league_player_ids, by = "player_id")

name_map_check <- player_id_lookup_norm_scoped %>%
  distinct(player_id, player_name_norm) %>%
  count(player_name_norm, name = "n") %>%
  filter(n > 1)

if (nrow(name_map_check) > 0) {
  print_results(name_map_check)

  collision_debug <- player_id_lookup_norm_scoped %>%
    semi_join(name_map_check, by = "player_name_norm") %>%
    arrange(player_name_norm, player_id)

  print_results(collision_debug)

  stop("Stopping: multiple in-league player_id values share the same normalised player name")
}

player_id_lookup_norm_dedup <- player_id_lookup_norm_scoped %>%
  distinct(player_id, player_name, player_name_norm)

player_price_history_sc <- player_price_history_2026_norm %>%
  inner_join(
    player_id_lookup_norm_dedup %>%
      select(player_id, player_name_sc = player_name, player_name_norm),
    by = "player_name_norm"
  ) %>%
  transmute(
    player_id,
    player_name = player_name_sc,
    year,
    round,
    score,
    mins,
    price
  ) %>%
  distinct(player_id, round, .keep_all = TRUE) %>%
  arrange(player_id, round)

price_match_discrepancies <- team_players_latest %>%
  distinct(user_team_id, round, player_id) %>%
  left_join(
    player_id_lookup,
    by = "player_id"
  ) %>%
  left_join(
    player_price_history_sc %>%
      distinct(player_id, round) %>%
      mutate(has_price = TRUE),
    by = c("player_id", "round")
  ) %>%
  mutate(
    has_price = coalesce(has_price, FALSE)
  ) %>%
  filter(!has_price) %>%
  arrange(round, user_team_id, player_id)

if (nrow(price_match_discrepancies) > 0) {
  print_results(price_match_discrepancies)
  stop("Stopping: unmatched player_id/round combinations remain in player_price_history_sc")
}

saveRDS(player_price_history_2026, path_player_price_history_2026)
saveRDS(players_cf_2026, path_players_cf_2026)
saveRDS(player_id_lookup, path_player_id_lookup)
saveRDS(player_price_history_sc, path_player_price_history_sc)
```

## 15. Build cash and team value by round

```{r}
starting_cap <- 11950000L

# Sum player prices to rebuild each squad's market value by round.
team_prices_by_round <- team_players_latest %>%
  distinct(user_team_id, round, player_id) %>%
  left_join(
    player_price_history_sc %>%
      select(player_id, round, price),
    by = c("player_id", "round")
  ) %>%
  group_by(user_team_id, round) %>%
  summarise(
    squad_size = n(),
    n_players_priced = sum(!is.na(price)),
    squad_value_calc = if_else(
      n_players_priced == squad_size,
      sum(price, na.rm = TRUE),
      NA_real_
    ),
    .groups = "drop"
  )

team_round_rosters <- team_players_latest %>%
  distinct(user_team_id, round, player_id)

min_round_available <- min(team_round_rosters$round, na.rm = TRUE)
max_round_available <- max(team_round_rosters$round, na.rm = TRUE)

# Identify players newly in a roster compared with the prior round.
team_ins <- team_round_rosters %>%
  filter(round > min_round_available) %>%
  anti_join(
    team_round_rosters %>%
      mutate(round = round + 1L),
    by = c("user_team_id", "round", "player_id")
  ) %>%
  rename(player_id_in = player_id)

# Identify players removed from a roster compared with the prior round.
team_outs <- team_round_rosters %>%
  filter(round < max_round_available) %>%
  mutate(round = round + 1L) %>%
  anti_join(
    team_round_rosters,
    by = c("user_team_id", "round", "player_id")
  ) %>%
  rename(player_id_out = player_id)

# Price trade events using the prior round's price point.
trade_events_priced <- team_ins %>%
  group_by(user_team_id, round) %>%
  mutate(trade_slot = row_number()) %>%
  ungroup() %>%
  full_join(
    team_outs %>%
      group_by(user_team_id, round) %>%
      mutate(trade_slot = row_number()) %>%
      ungroup(),
    by = c("user_team_id", "round", "trade_slot")
  ) %>%
  left_join(
    player_price_history_sc %>%
      transmute(
        player_id_in = player_id,
        round = round + 1L,
        buy_price = price
      ),
    by = c("player_id_in", "round")
  ) %>%
  left_join(
    player_price_history_sc %>%
      transmute(
        player_id_out = player_id,
        round = round + 1L,
        sell_price = price
      ),
    by = c("player_id_out", "round")
  ) %>%
  mutate(
    cash_delta = coalesce(sell_price, 0) - coalesce(buy_price, 0)
  )

trade_cash_by_round <- trade_events_priced %>%
  group_by(user_team_id, round) %>%
  summarise(
    trade_ins = sum(!is.na(player_id_in)),
    trade_outs = sum(!is.na(player_id_out)),
    total_buy_price = sum(coalesce(buy_price, 0), na.rm = TRUE),
    total_sell_price = sum(coalesce(sell_price, 0), na.rm = TRUE),
    cash_delta = sum(cash_delta, na.rm = TRUE),
    .groups = "drop"
  )

initial_cash_by_team <- team_prices_by_round %>%
  group_by(user_team_id) %>%
  slice_min(round, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  transmute(
    user_team_id,
    initial_squad_value_calc = squad_value_calc,
    initial_cash_calc = starting_cap - squad_value_calc
  )

cash_by_round <- team_prices_by_round %>%
  left_join(trade_cash_by_round, by = c("user_team_id", "round")) %>%
  left_join(initial_cash_by_team, by = "user_team_id") %>%
  arrange(user_team_id, round) %>%
  group_by(user_team_id) %>%
  mutate(
    trade_ins = coalesce(trade_ins, 0L),
    trade_outs = coalesce(trade_outs, 0L),
    total_buy_price = coalesce(total_buy_price, 0),
    total_sell_price = coalesce(total_sell_price, 0),
    cash_delta = coalesce(cash_delta, 0),
    cash_end_round_calc = initial_cash_calc + cumsum(cash_delta),
    team_value_total_calc = squad_value_calc + cash_end_round_calc
  ) %>%
  ungroup()

negative_cash_check <- cash_by_round %>%
  filter(cash_end_round_calc < 0)

if (nrow(negative_cash_check) > 0) {
  print_results(negative_cash_check)
  stop("Stopping: negative cash balances remain after applying previous-round trade pricing")
}
```

## 16. Attach value fields back to ladder history safely

```{r}
# Build one comparison row per team-round to avoid duplicated joins on reruns.
ladder_value_compare <- ladder_history %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(user_team_id, round, squad_value) %>%
  left_join(
    cash_by_round %>%
      select(
        user_team_id,
        round,
        squad_size,
        n_players_priced,
        squad_value_calc,
        initial_cash_calc,
        trade_ins,
        trade_outs,
        total_buy_price,
        total_sell_price,
        cash_delta,
        cash_end_round_calc,
        team_value_total_calc
      ),
    by = c("user_team_id", "round")
  ) %>%
  mutate(
    squad_value_diff = squad_value_calc - squad_value
  )

ladder_history <- ladder_history %>%
  select(
    -any_of(c(
      "squad_size",
      "n_players_priced",
      "squad_value_calc",
      "initial_cash_calc",
      "trade_ins",
      "trade_outs",
      "total_buy_price",
      "total_sell_price",
      "cash_delta",
      "cash_end_round_calc",
      "team_value_total_calc",
      "squad_value_diff"
    ))
  ) %>%
  left_join(
    ladder_value_compare %>%
      select(
        user_team_id,
        round,
        squad_size,
        n_players_priced,
        squad_value_calc,
        initial_cash_calc,
        trade_ins,
        trade_outs,
        total_buy_price,
        total_sell_price,
        cash_delta,
        cash_end_round_calc,
        team_value_total_calc,
        squad_value_diff
      ),
    by = c("user_team_id", "round")
  )

saveRDS(ladder_history, path_ladder_history)
```

## 17. Final returned objects

```{r}
list(
  current_round = current_round,
  rounds_pulled = rounds_to_pull,
  ladder_history = ladder_history,
  team_players_latest = team_players_latest,
  inferred_changes = inferred_changes,
  grog_baguettes_latest = grog_baguettes_latest,
  grog_baguettes_changes = grog_baguettes_changes,
  league_change_summary = league_change_summary,
  run_log = run_log,
  team_round_results = team_round_results,
  team_prices_by_round = team_prices_by_round,
  trade_events_priced = trade_events_priced,
  trade_cash_by_round = trade_cash_by_round,
  cash_by_round = cash_by_round,
  ladder_value_compare = ladder_value_compare
)
```

## 18. Optional example output

```{r}
ladder_history_latest <- ladder_history %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup()

ladder_history_latest %>%
  filter(
    round == 5,
    coach_name != "Greg"
  ) %>%
  transmute(
    coach_name,
    team_name,
    cash_end_round_calc_num = cash_end_round_calc,
    cash_end_round_calc = paste0("$", format(cash_end_round_calc, big.mark = ",", scientific = FALSE))
  ) %>%
  arrange(desc(cash_end_round_calc_num)) %>%
  select(-cash_end_round_calc_num)
```
