---
title: "Ingest local league data and tracking"
output: html_document
---

## Purpose

This Rmd pulls authenticated SuperCoach league data, stores historical snapshots safely across reruns, rebuilds the latest known team state, preserves the verified cash-per-round logic, and emits checklist-oriented lookup tables using only confirmed production sources.

## Outputs

This script writes the following `.rds` files under the league-specific data folder:

- `ladder_history.rds`
- `fixtures_history.rds`
- `fixture_triggers.rds`
- `team_players_snapshots.rds`
- `team_players_latest.rds`
- `team_round_signatures.rds`
- `team_round_stats_history.rds`
- `actual_trade_history.rds`
- `inferred_changes.rds`
- `competition_state_history.rds`
- `nrl_fixture_source_history.rds`
- `nrl_team_context_history.rds`
- `players_cf_history.rds`
- `players_cf_latest.rds`
- `player_history_refresh_log.rds`
- `source_refresh_log.rds`
- `run_log.rds`
- `player_price_history_2026.rds`
- `players_cf_2026.rds`
- `player_id_lookup.rds`
- `player_price_history_sc.rds`
- `master_player_round_latest.rds`
- `opponent_behaviour_history.rds`
- `squad_round_enriched.rds`
- `game_rules_round_state.rds`
- `player_scoring_component_history.rds`
- `team_list_role_certainty.rds`
- `fixture_matchup_table.rds`
- `team_performance_context.rds`
- `cash_generation_model.rds`
- `league_ownership_movement.rds`
- `availability_risk_table.rds`
- `captaincy_vc_table.rds`
- `structure_health_table.rds`
- `scenario_refresh_table.rds`
- `long_horizon_planning_table.rds`
- `checklist_coverage_status.rds`

## 1. Setup

```{r}
suppressPackageStartupMessages({
  library(jsonlite)
  library(dplyr)
  library(tibble)
  library(purrr)
  library(tidyr)
  library(stringr)
  library(knitr)
})
```

## 2. Configuration

```{r}
league_id <- 21064L
season_rounds <- 1:27
base_url <- "https://www.supercoach.com.au/2026/api/nrl/classic/v1"
run_ts <- Sys.time()
season_year <- 2026L

if (!nzchar(Sys.getenv("SC_BEARER"))) {
  stop("SC_BEARER must be set in the environment before rendering this Rmd")
}

data_dir <- file.path("data", paste0("supercoach_league_", league_id))
dir.create(data_dir, recursive = TRUE, showWarnings = FALSE)

path_ladder_history <- file.path(data_dir, "ladder_history.rds")
path_fixtures_history <- file.path(data_dir, "fixtures_history.rds")
path_fixture_triggers <- file.path(data_dir, "fixture_triggers.rds")
path_team_players_snapshots <- file.path(data_dir, "team_players_snapshots.rds")
path_team_players_latest <- file.path(data_dir, "team_players_latest.rds")
path_team_round_signatures <- file.path(data_dir, "team_round_signatures.rds")
path_team_round_stats_history <- file.path(data_dir, "team_round_stats_history.rds")
path_actual_trade_history <- file.path(data_dir, "actual_trade_history.rds")
path_inferred_changes <- file.path(data_dir, "inferred_changes.rds")
path_competition_state_history <- file.path(data_dir, "competition_state_history.rds")
path_nrl_fixture_source_history <- file.path(data_dir, "nrl_fixture_source_history.rds")
path_nrl_team_context_history <- file.path(data_dir, "nrl_team_context_history.rds")
path_players_cf_history <- file.path(data_dir, "players_cf_history.rds")
path_players_cf_latest <- file.path(data_dir, "players_cf_latest.rds")
path_player_history_refresh_log <- file.path(data_dir, "player_history_refresh_log.rds")
path_source_refresh_log <- file.path(data_dir, "source_refresh_log.rds")
path_run_log <- file.path(data_dir, "run_log.rds")
path_player_price_history_2026 <- file.path(data_dir, "player_price_history_2026.rds")
path_players_cf_2026 <- file.path(data_dir, "players_cf_2026.rds")
path_player_id_lookup <- file.path(data_dir, "player_id_lookup.rds")
path_player_price_history_sc <- file.path(data_dir, "player_price_history_sc.rds")
path_master_player_round_latest <- file.path(data_dir, "master_player_round_latest.rds")
path_opponent_behaviour_history <- file.path(data_dir, "opponent_behaviour_history.rds")
path_squad_round_enriched <- file.path(data_dir, "squad_round_enriched.rds")
path_game_rules_round_state <- file.path(data_dir, "game_rules_round_state.rds")
path_player_scoring_component_history <- file.path(data_dir, "player_scoring_component_history.rds")
path_team_list_role_certainty <- file.path(data_dir, "team_list_role_certainty.rds")
path_fixture_matchup_table <- file.path(data_dir, "fixture_matchup_table.rds")
path_team_performance_context <- file.path(data_dir, "team_performance_context.rds")
path_cash_generation_model <- file.path(data_dir, "cash_generation_model.rds")
path_league_ownership_movement <- file.path(data_dir, "league_ownership_movement.rds")
path_availability_risk_table <- file.path(data_dir, "availability_risk_table.rds")
path_captaincy_vc_table <- file.path(data_dir, "captaincy_vc_table.rds")
path_structure_health_table <- file.path(data_dir, "structure_health_table.rds")
path_scenario_refresh_table <- file.path(data_dir, "scenario_refresh_table.rds")
path_long_horizon_planning_table <- file.path(data_dir, "long_horizon_planning_table.rds")
path_checklist_coverage_status <- file.path(data_dir, "checklist_coverage_status.rds")
```

## 3. Helper functions

```{r}
`%||%` <- function(a, b) {
  if (is.null(a) || length(a) == 0) b else a
}

read_rds_if_exists <- function(path, default) {
  if (file.exists(path)) readRDS(path) else default
}

normalise_player_name <- function(x) {
  x %>%
    stringr::str_to_lower() %>%
    stringr::str_replace_all("\\*+", " ") %>%
    stringr::str_replace_all("[`´‘’']", "") %>%
    stringr::str_replace_all("[^a-z0-9, ]", " ") %>%
    stringr::str_squish() %>%
    stringr::str_replace_all(" ", "")
}

normalise_team_name <- function(x) {
  out <- x %>%
    stringr::str_to_lower() %>%
    stringr::str_replace_all("&amp;", "and") %>%
    stringr::str_replace_all("[^a-z0-9]", "")

  out[out == "weststigers"] <- "tigers"
  out[out == "canterburybankstownbulldogs"] <- "bulldogs"
  out
}

coalesce_chr <- function(x) {
  x <- as.character(x)
  x[is.na(x)] <- ""
  x
}

safe_chr <- function(x, default = NA_character_) {
  if (is.null(x) || length(x) == 0) return(default)
  as.character(x[[1]])
}

safe_int <- function(x, default = NA_integer_) {
  if (is.null(x) || length(x) == 0) return(default)
  suppressWarnings(as.integer(x[[1]]))
}

safe_dbl <- function(x, default = NA_real_) {
  if (is.null(x) || length(x) == 0) return(default)
  suppressWarnings(as.numeric(x[[1]]))
}

safe_lgl <- function(x, default = NA) {
  if (is.null(x) || length(x) == 0) return(default)
  as.logical(x[[1]])
}

safe_posixct <- function(x, default = as.POSIXct(NA)) {
  if (is.null(x) || length(x) == 0) return(default)
  value <- as.character(x[[1]])

  parsed <- suppressWarnings(
    as.POSIXct(value, format = "%Y-%m-%dT%H:%M:%OSZ", tz = "UTC")
  )

  if (is.na(parsed)) {
    parsed <- suppressWarnings(as.POSIXct(value, tz = "UTC"))
  }

  if (is.na(parsed)) default else parsed
}

list_to_chr <- function(x) {
  if (length(x) == 0) return(NA_character_)
  paste(as.character(unlist(x)), collapse = ", ")
}

build_url <- function(base, query = list()) {
  query <- query[!vapply(query, is.null, logical(1))]
  if (length(query) == 0) {
    return(base)
  }

  encoded <- purrr::imap_chr(
    query,
    ~ paste0(
      utils::URLencode(.y, reserved = TRUE),
      "=",
      utils::URLencode(as.character(.x), reserved = TRUE)
    )
  )

  paste0(base, "?", paste(encoded, collapse = "&"))
}

sc_headers <- function() {
  c(
    Accept = "application/json",
    Authorization = paste("Bearer", Sys.getenv("SC_BEARER")),
    Referer = paste0(
      "https://www.supercoach.com.au/nrl/classic/leagues(popup:leagues/",
      league_id,
      "/head-2-head)"
    ),
    Origin = "https://www.supercoach.com.au",
    "User-Agent" = "Mozilla/5.0"
  )
}

stats_headers <- function() {
  c("User-Agent" = "Mozilla/5.0")
}

http_get_text <- function(url, headers = character()) {
  con <- base::url(url, headers = headers)
  on.exit(try(close(con), silent = TRUE), add = TRUE)
  paste(readLines(con, warn = FALSE), collapse = "\n")
}

sc_get_json <- function(path, query = list()) {
  url <- build_url(paste0(base_url, path), query)
  txt <- http_get_text(url, sc_headers())
  jsonlite::fromJSON(txt, simplifyVector = FALSE)
}

stats_get_json <- function(url, query = list()) {
  full_url <- build_url(url, query)
  txt <- http_get_text(full_url, stats_headers())
  jsonlite::fromJSON(txt, simplifyVector = FALSE)
}

bind_rows_safe <- function(x) {
  if (is.null(x) || length(x) == 0) {
    tibble()
  } else {
    bind_rows(x)
  }
}

parallel_map <- function(x, f, mc.cores = max(1L, min(6L, parallel::detectCores() - 1L))) {
  if (length(x) <= 1 || .Platform$OS.type == "windows" || mc.cores <= 1) {
    return(lapply(x, f))
  }
  parallel::mclapply(x, f, mc.cores = mc.cores)
}

roll_mean_right <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) < k) return(out)
  for (i in seq.int(k, length(x))) {
    window <- x[(i - k + 1):i]
    if (all(!is.na(window))) {
      out[i] <- mean(window)
    }
  }
  out
}

roll_mean_prev_non_na <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) == 0) return(out)

  for (i in seq_along(x)) {
    if (i == 1) next
    start_idx <- max(1L, i - k)
    window <- x[start_idx:(i - 1L)]
    window <- window[!is.na(window)]
    if (length(window) > 0) {
      out[i] <- mean(window)
    }
  }

  out
}

lookahead_mean_non_na <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) == 0) return(out)

  for (i in seq_along(x)) {
    end_idx <- min(length(x), i + k - 1L)
    window <- x[i:end_idx]
    window <- window[!is.na(window)]
    if (length(window) > 0) {
      out[i] <- mean(window)
    }
  }

  out
}

roll_sd_right <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) < k) return(out)
  for (i in seq.int(k, length(x))) {
    window <- x[(i - k + 1):i]
    if (sum(!is.na(window)) >= 2) {
      out[i] <- stats::sd(window, na.rm = TRUE)
    }
  }
  out
}

roll_min_right <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) < k) return(out)
  for (i in seq.int(k, length(x))) {
    window <- x[(i - k + 1):i]
    if (all(!is.na(window))) {
      out[i] <- min(window)
    }
  }
  out
}

roll_max_right <- function(x, k) {
  out <- rep(NA_real_, length(x))
  if (length(x) < k) return(out)
  for (i in seq.int(k, length(x))) {
    window <- x[(i - k + 1):i]
    if (all(!is.na(window))) {
      out[i] <- max(window)
    }
  }
  out
}

build_roster_signature <- function(df) {
  if (nrow(df) == 0 || !"player_id" %in% names(df)) return(NA_character_)

  df %>%
    transmute(
      sig = paste(
        coalesce_chr(player_id),
        coalesce_chr(position),
        coalesce_chr(position_long),
        coalesce_chr(position_sort),
        coalesce_chr(picked),
        sep = "::"
      )
    ) %>%
    arrange(sig) %>%
    pull(sig) %>%
    paste(collapse = "|")
}

extract_roster_membership <- function(df) {
  if (nrow(df) == 0 || !"player_id" %in% names(df)) {
    return(tibble(player_id = integer()))
  }

  df %>%
    filter(!is.na(player_id)) %>%
    distinct(player_id) %>%
    arrange(player_id)
}

pair_inferred_trades <- function(players_out, players_in) {
  n_out <- length(players_out)
  n_in <- length(players_in)
  n_pair <- min(n_out, n_in)

  tibble(
    trade_seq = seq_len(n_pair),
    player_out_id = if (n_pair > 0) players_out[seq_len(n_pair)] else integer(),
    player_in_id = if (n_pair > 0) players_in[seq_len(n_pair)] else integer()
  )
}

get_settings <- function() {
  sc_get_json("/settings")
}

get_me <- function() {
  sc_get_json("/me")
}

get_teams <- function() {
  sc_get_json("/teams")
}

get_ladder_fixtures_round <- function(round_value) {
  x <- sc_get_json(
    paste0("/leagues/", league_id, "/ladderAndFixtures"),
    query = list(round = round_value)
  )

  ladder_tbl <- purrr::map_dfr(x$ladder %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      league_id = safe_int(z$league_id, league_id),
      round = safe_int(z$round, round_value),
      user_team_id = safe_int(z$user_team_id),
      team_name = safe_chr(z$userTeam$teamname),
      coach_name = safe_chr(z$userTeam$user$first_name),
      is_me = safe_lgl(z$userTeam$user$is_me, FALSE),
      wins = safe_dbl(z$wins),
      losses = safe_dbl(z$losses),
      draws = safe_dbl(z$draws),
      ladder_points = safe_dbl(z$points),
      points_for = safe_dbl(z$points_for),
      points_against = safe_dbl(z$points_against),
      position = safe_dbl(z$position),
      last_position = safe_dbl(z$last_position),
      wins_last5 = safe_dbl(z$wins_last5),
      losses_last5 = safe_dbl(z$losses_last5),
      draws_last5 = safe_dbl(z$draws_last5),
      round_points = safe_dbl(z$userTeam$stats[[1]]$points),
      total_points = safe_dbl(z$userTeam$stats[[1]]$total_points),
      overall_position = safe_dbl(z$userTeam$stats[[1]]$position),
      round_position = safe_dbl(z$userTeam$stats[[1]]$round_position),
      squad_value = safe_dbl(z$userTeam$stats[[1]]$price),
      price_change = safe_dbl(z$userTeam$stats[[1]]$price_change),
      total_price_change = safe_dbl(z$userTeam$stats[[1]]$total_price_change),
      rounds_played = safe_dbl(z$userTeam$stats[[1]]$rounds_played)
    )
  })

  fixtures_tbl <- purrr::map_dfr(x$fixtures %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      league_id = league_id,
      round = safe_int(z$round, round_value),
      fixture = safe_int(z$fixture),
      fixture_id = paste0("league_", safe_int(z$round, round_value), "_", safe_int(z$fixture)),
      user_team1_id = safe_int(z$user_team1$id),
      user_team1_name = safe_chr(z$user_team1$teamname),
      user_team1_coach = safe_chr(z$user_team1$user$first_name),
      user_team1_points = safe_dbl(z$user_team1$stats[[1]]$points),
      user_team2_id = safe_int(z$user_team2$id),
      user_team2_name = safe_chr(z$user_team2$teamname),
      user_team2_coach = safe_chr(z$user_team2$user$first_name),
      user_team2_points = safe_dbl(z$user_team2$stats[[1]]$points)
    )
  })

  list(ladder = ladder_tbl, fixtures = fixtures_tbl)
}

get_stats_players_round <- function(team_id, round_value) {
  x <- sc_get_json(
    paste0("/userteams/", team_id, "/statsPlayers"),
    query = list(round = round_value)
  )

  players_tbl <- purrr::map_dfr(x$players %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      user_team_id = safe_int(z$user_team_id, team_id),
      round = safe_int(z$round, round_value),
      player_id = safe_int(z$player_id),
      picked = safe_lgl(z$picked, FALSE),
      position = safe_chr(z$position),
      updated = safe_chr(z$updated),
      position_long = safe_chr(z$position_long),
      position_sort = safe_int(z$position_sort)
    )
  })

  stats_tbl <- purrr::map_dfr(x$stats %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      user_team_id = safe_int(z$user_team_id, team_id),
      round = safe_int(z$round, round_value),
      salarycap = safe_dbl(z$salarycap),
      points = safe_dbl(z$points),
      total_points = safe_dbl(z$total_points),
      position = safe_dbl(z$position),
      last_position = safe_dbl(z$last_position),
      round_position = safe_dbl(z$round_position),
      price = safe_dbl(z$price),
      price_change = safe_dbl(z$price_change),
      total_price_change = safe_dbl(z$total_price_change),
      rounds_played = safe_dbl(z$rounds_played),
      changes = safe_int(z$changes),
      total_changes = safe_int(z$total_changes),
      trade_boosts_used = safe_int(z$trade_boosts_used),
      last_trade_boosts_used = safe_int(z$last_trade_boosts_used),
      league_wins = safe_int(z$league_wins),
      league_draws = safe_int(z$league_draws),
      league_losses = safe_int(z$league_losses)
    )
  })

  trades_tbl <- purrr::map_dfr(x$trades %||% list(), function(z) {
    tibble(
      run_ts = run_ts,
      round = safe_int(z$round, round_value),
      user_team_id = safe_int(z$user_id, team_id),
      buy_player_id = safe_int(z$buy_player_id),
      sell_player_id = safe_int(z$sell_player_id),
      trade_source = "actual_api"
    )
  })

  list(players = players_tbl, stats = stats_tbl, trades = trades_tbl)
}

extract_initialvalue_catalog <- function(year = season_year) {
  x <- stats_get_json(
    "https://www.nrlsupercoachstats.com/initialvalue.php",
    query = list(
      year = year,
      grid_id = "list1",
      jqgrid_page = 1,
      rows = 2000,
      search = "false"
    )
  )

  rows <- bind_rows(x$rows %||% list())
  rows %>%
    transmute(
      player_name = Name %>%
        gsub("^.*?>", "", .) %>%
        gsub("</a>$", "", .),
      team_abbrev = Team,
      posn1 = Posn1,
      posn2 = ifelse(Posn2 == "", NA_character_, Posn2),
      positions = ifelse(is.na(posn2), posn1, paste(posn1, posn2, sep = "/")),
      current_price_external = suppressWarnings(as.numeric(Price)),
      avg_score_external = suppressWarnings(as.numeric(AvgScore)),
      projected_price_next = suppressWarnings(as.numeric(ProjectedPrice))
    ) %>%
    distinct(player_name, .keep_all = TRUE) %>%
    arrange(player_name)
}

get_yearplot_player <- function(player_name, year = season_year) {
  stats_get_json(
    "https://www.nrlsupercoachstats.com/highcharts/data-yearplot.php",
    query = list(dropdown1 = player_name, YEAR = year)
  )
}

yearplot_to_tibble_year <- function(x, player_name, year = season_year) {
  if (length(x) == 0) {
    return(tibble(
      player_name = character(),
      year = integer(),
      round = integer(),
      score = numeric(),
      mins = numeric(),
      price = numeric()
    ))
  }

  rounds <- suppressWarnings(as.integer(unlist(x[[1]]$data)))
  out <- tibble(player_name = player_name, year = year, round = rounds)

  for (i in seq_along(x)[-1]) {
    nm <- safe_chr(x[[i]]$name, "")
    vals <- suppressWarnings(as.numeric(unlist(x[[i]]$data)))

    if (identical(nm, paste0(year, "Score"))) out$score <- vals
    if (identical(nm, paste0(year, "Mins"))) out$mins <- vals
    if (identical(nm, paste0(year, "Price"))) out$price <- vals
  }

  out
}

safe_get_price_history <- function(player_name, year = season_year) {
  tryCatch(
    {
      get_yearplot_player(player_name, year) %>%
        yearplot_to_tibble_year(player_name = player_name, year = year)
    },
    error = function(e) {
      tibble(
        player_name = player_name,
        year = year,
        round = integer(),
        score = numeric(),
        mins = numeric(),
        price = numeric()
      )
    }
  )
}

print_results <- function(x, n = 10) {
  print(utils::head(as.data.frame(x), n = n), row.names = FALSE)
}
```

## 4. Refresh Source Logs

```{r}
source("scripts/refresh_supercoach_logs.R", local = TRUE)
refresh_ctx <- refresh_supercoach_logs()
list2env(refresh_ctx, envir = environment())
```

## 13. Build lookup tables from confirmed sources

```{r}
player_price_rollups <- player_price_history_sc %>%
  arrange(player_id, round) %>%
  group_by(player_id) %>%
  mutate(
    played_round_flag = !is.na(score) & (round < current_round | coalesce(mins, 0) > 0 | score != 0),
    score_for_rollups = if_else(played_round_flag, score, NA_real_),
    season_average = if_else(
      cumsum(played_round_flag) > 0,
      cumsum(coalesce(score_for_rollups, 0)) / cumsum(played_round_flag),
      NA_real_
    ),
    avg_3 = roll_mean_right(score_for_rollups, 3),
    avg_5 = roll_mean_right(score_for_rollups, 5),
    volatility_score = roll_sd_right(score_for_rollups, 5),
    floor_score_estimate = roll_min_right(score_for_rollups, 5),
    ceiling_score_estimate = roll_max_right(score_for_rollups, 5),
    games_played = cumsum(played_round_flag),
    total_points = cumsum(coalesce(score_for_rollups, 0)),
    price_change_last_round = price - lag(price),
    cumulative_cash_generation = price - first(price)
  ) %>%
  ungroup()

latest_price_rollups <- player_price_rollups %>%
  filter(round <= current_round) %>%
  group_by(player_id) %>%
  slice_max(round, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(
    player_id,
    latest_round = round,
    current_price_history = price,
    season_average,
    avg_3,
    avg_5,
    games_played,
    total_points,
    price_change_last_round,
    cumulative_cash_generation
  )

player_history_lists <- player_price_history_sc %>%
  arrange(player_id, round) %>%
  group_by(player_id) %>%
  summarise(
    points_history = list(tibble(round = round, score = score)),
    minute_history = list(tibble(round = round, mins = mins)),
    price_history = list(tibble(round = round, price = price)),
    .groups = "drop"
  )

master_player_round_latest <- player_catalog %>%
  left_join(initialvalue_catalog, by = c("full_name" = "player_name", "team_abbrev", "name_norm")) %>%
  left_join(latest_price_rollups, by = "player_id") %>%
  left_join(player_history_lists, by = "player_id") %>%
  transmute(
    run_ts = run_ts,
    player_id,
    full_name,
    team = coalesce(team_abbrev, team_name),
    positions = positions,
    current_price = coalesce(current_price_history, current_price_external),
    breakeven = NA_real_,
    current_season_average = season_average,
    average_3_round = avg_3,
    average_5_round = avg_5,
    ownership_percentage = NA_real_,
    total_points,
    games_played,
    status = case_when(
      !is.na(injury_suspension_status_text) ~ injury_suspension_status_text,
      !active_flag ~ "inactive",
      TRUE ~ played_status_display
    ),
    injury_detail = injury_suspension_status_text,
    expected_return = NA_character_,
    role_tag = NA_character_,
    goal_kicking_status = NA_character_,
    starting_status = NA_character_,
    locked_flag,
    played_status,
    active_flag,
    minute_history,
    points_history,
    price_history
  )

player_scoring_component_history <- player_price_rollups %>%
  transmute(
    run_ts = run_ts,
    player_id,
    round,
    total_score = score,
    base_stats = NA_real_,
    base_attack = NA_real_,
    tries = NA_real_,
    try_assists = NA_real_,
    linebreaks = NA_real_,
    linebreak_assists = NA_real_,
    tackle_busts = NA_real_,
    offloads = NA_real_,
    goals = NA_real_,
    kick_metres = NA_real_,
    tackles_made = NA_real_,
    missed_tackles = NA_real_,
    run_metres = NA_real_,
    errors = NA_real_,
    disruptions = NA_character_,
    minutes_played = mins,
    starting_position_that_round = NA_character_,
    base_per_minute = NA_real_,
    attack_reliance_ratio = NA_real_,
    volatility_score = volatility_score,
    floor_score_estimate = floor_score_estimate,
    ceiling_score_estimate = ceiling_score_estimate,
    role_adjusted_average = NA_real_,
    points_per_minute = if_else(!is.na(mins) & mins > 0, score / mins, NA_real_)
  )

availability_risk_table <- player_catalog %>%
  transmute(
    run_ts = run_ts,
    player_id,
    full_name,
    team_abbrev,
    locked_flag,
    played_status,
    played_status_display,
    active_flag,
    injury_suspension_status,
    injury_suspension_status_text,
    expected_return = NA_character_,
    risk_band = case_when(
      !is.na(injury_suspension_status) ~ "high",
      active_flag & locked_flag ~ "medium",
      active_flag ~ "low",
      TRUE ~ "high"
    )
  )

my_round_state <- team_round_stats_history %>%
  filter(user_team_id == grog_baguettes_team_id) %>%
  group_by(round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup()

position_rules_tbl <- bind_rows_safe(settings$game$positions) %>%
  transmute(
    position_id = as.character(id),
    position_name = as.character(name),
    position_sort = as.integer(sort),
    max_players = as.integer(max_players),
    active_max_players = as.integer(active_max_players)
  )

game_rules_round_state <- tibble(
  run_ts = run_ts,
  league_id = league_id,
  settings_current_round = settings_current_round,
  settings_next_round = settings_next_round,
  current_round = current_round,
  next_round = next_round,
  round_inference_source = round_inference_source,
  round_closed_through_utc = round_closed_through_utc,
  competition_status = competition_status,
  is_lockout = safe_lgl(settings$competition$is_lockout, FALSE),
  is_partial_lockout = safe_lgl(settings$competition$is_partial_lockout, FALSE),
  lockout_start = safe_chr(settings$competition$lockout_start),
  lockout_end = safe_chr(settings$competition$lockout_end),
  rolling_lockout = safe_lgl(settings$game$rolling_lockout, FALSE),
  squad_size = safe_int(settings$game$max_players_for_team),
  selected_slots = sum(position_rules_tbl$active_max_players, na.rm = TRUE) + safe_int(settings$game$game_num_emergencies, 0L),
  emergency_slots = safe_int(settings$game$game_num_emergencies),
  max_total_trades = safe_int(settings$game$game_max_total_changes),
  max_round_trades_without_boost = safe_int(settings$game$game_max_changes),
  trades_used_to_date = my_round_state %>% filter(round == current_round) %>% pull(total_changes) %>% { if (length(.) == 0) NA_integer_ else .[[1]] },
  trades_remaining = safe_int(settings$game$game_max_total_changes) - coalesce(
    my_round_state %>% filter(round == current_round) %>% pull(total_changes) %>% { if (length(.) == 0) NA_integer_ else .[[1]] },
    0L
  ),
  max_boosts = safe_int(settings$game$max_boosts),
  boosts_used_to_date = my_round_state %>% filter(round == current_round) %>% pull(trade_boosts_used) %>% { if (length(.) == 0) NA_integer_ else .[[1]] },
  boosts_remaining = safe_int(settings$game$max_boosts) - coalesce(
    my_round_state %>% filter(round == current_round) %>% pull(trade_boosts_used) %>% { if (length(.) == 0) NA_integer_ else .[[1]] },
    0L
  ),
  dual_position_enabled = safe_lgl(settings$game$dual_position_players, FALSE),
  bye_round_structure = list(unlist(settings$game$show_bye_rounds %||% list())),
  real_bye_rounds = list(unlist(settings$game$real_bye_rounds %||% list())),
  finals_round = safe_int(settings$game$game_finals_round),
  scoring_round_end = safe_int(settings$game$final_scoring_round),
  price_rounding = safe_int(settings$game$rounding_price),
  position_rules = list(position_rules_tbl),
  player_lock_state = list(availability_risk_table %>% select(player_id, full_name, locked_flag, played_status, played_status_display))
)

fixture_triggers <- tibble(
  run_ts = run_ts,
  settings_current_round = settings_current_round,
  settings_next_round = settings_next_round,
  current_round = current_round,
  next_round = next_round,
  round_inference_source = round_inference_source,
  round_closed_through_utc = round_closed_through_utc,
  lockout_start = safe_chr(settings$competition$lockout_start),
  lockout_end = safe_chr(settings$competition$lockout_end),
  competition_status = competition_status
)

# Team-list certainty is still derived from SuperCoach squad snapshots.
# It is useful for spot checks, but it is not yet an official Tuesday team list / Friday late-mail feed.
team_list_role_certainty <- team_players_latest %>%
  left_join(
    player_price_history_sc %>%
      group_by(player_id) %>%
      arrange(round, .by_group = TRUE) %>%
      mutate(likely_minutes = roll_mean_right(mins, 3)) %>%
      ungroup() %>%
      select(player_id, round, mins, likely_minutes),
    by = c("player_id", "round")
  ) %>%
  mutate(
    named_flag = TRUE,
    jersey_number = if_else(!is.na(position_sort), as.integer(position_sort), NA_integer_),
    starting_or_bench = case_when(
      !is.na(position_sort) & position_sort <= 17 ~ "selected",
      !is.na(position_sort) & position_sort > 17 ~ "reserve",
      TRUE ~ "unknown"
    ),
    listed_position = position,
    actual_recent_role = position_long,
    role_change_likelihood = case_when(
      !is.na(likely_minutes) & likely_minutes < 25 ~ "high",
      !is.na(likely_minutes) & likely_minutes < 45 ~ "medium",
      !is.na(likely_minutes) ~ "low",
      TRUE ~ NA_character_
    ),
    likely_late_omission = NA_character_,
    likely_replacement = NA_character_,
    injury_cover_flag = NA,
    return_threat_flag = NA
  ) %>%
  select(
    run_ts, user_team_id, round, player_id, named_flag, jersey_number,
    starting_or_bench, listed_position, actual_recent_role, likely_minutes,
    role_change_likelihood, likely_late_omission, likely_replacement,
    injury_cover_flag, return_threat_flag
  )

# Real NRL fixture context comes from official NRL draw and ladder pages.
latest_nrl_fixture_source <- nrl_fixture_source_history %>%
  group_by(round, team_abbrev) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup()

latest_nrl_team_context_source <- nrl_team_context_history %>%
  group_by(round, team_abbrev) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup()

nrl_home_reference <- tibble(
  team_abbrev = c("BRO", "BUL", "CBR", "DOL", "GCT", "MEL", "MNL", "NEW", "NQC", "NZL", "PAR", "PTH", "SHA", "STG", "STH", "SYD", "WST"),
  home_region = c("brisbane", "sydney", "canberra", "brisbane", "goldcoast", "melbourne", "sydney", "newcastle", "townsville", "auckland", "sydney", "sydney", "sydney", "wollongong", "sydney", "sydney", "sydney")
)

venue_region_reference <- tibble(
  venue_city = c("Auckland", "Brisbane", "Canberra", "Coffs Harbour", "Darwin", "Gold Coast", "Melbourne", "Mudgee", "Newcastle", "Perth", "Redcliffe", "Sydney", "Townsville", "Wollongong"),
  venue_region = c("auckland", "brisbane", "canberra", "regional_nsw", "darwin", "goldcoast", "melbourne", "regional_nsw", "newcastle", "perth", "brisbane", "sydney", "townsville", "wollongong")
)

team_schedule <- latest_nrl_fixture_source %>%
  left_join(nrl_home_reference, by = "team_abbrev") %>%
  left_join(venue_region_reference, by = "venue_city") %>%
  arrange(team_abbrev, round, kickoff_at_utc) %>%
  group_by(team_abbrev) %>%
  mutate(
    days_rest = as.numeric(difftime(kickoff_at_utc, lag(kickoff_at_utc), units = "days")),
    travel_burden = case_when(
      bye_flag %in% TRUE ~ "bye",
      home_away == "home" ~ "home",
      is.na(venue_region) | is.na(home_region) ~ NA_character_,
      venue_region == home_region ~ "low",
      home_region == "sydney" & venue_region %in% c("wollongong", "newcastle", "regional_nsw", "canberra") ~ "medium",
      home_region %in% c("brisbane", "goldcoast") & venue_region %in% c("brisbane", "goldcoast") ~ "medium",
      TRUE ~ "high"
    ),
    short_turnaround_flag = !is.na(days_rest) & days_rest < 6
  ) %>%
  ungroup()

team_results_by_round <- team_schedule %>%
  mutate(
    points_scored = if_else(match_state == "FullTime", team_score, NA_real_),
    points_conceded = if_else(match_state == "FullTime", opponent_score, NA_real_),
    result_points = case_when(
      is.na(points_scored) | is.na(points_conceded) ~ NA_real_,
      points_scored > points_conceded ~ 1,
      points_scored < points_conceded ~ 0,
      TRUE ~ 0.5
    )
  ) %>%
  arrange(team_abbrev, round, kickoff_at_utc) %>%
  group_by(team_abbrev) %>%
  mutate(
    attacking_trend_last_3 = roll_mean_prev_non_na(points_scored, 3),
    attacking_trend_last_5 = roll_mean_prev_non_na(points_scored, 5),
    defensive_trend_last_3 = roll_mean_prev_non_na(points_conceded, 3),
    defensive_trend_last_5 = roll_mean_prev_non_na(points_conceded, 5),
    recent_form_last_3 = roll_mean_prev_non_na(result_points, 3)
  ) %>%
  ungroup()

team_performance_context <- team_results_by_round %>%
  left_join(
    latest_nrl_team_context_source %>%
      select(
        round, team_abbrev, ladder_position, ladder_points, points_difference,
        streak, form, home_record, away_record, day_record, night_record,
        players_used, premiership_odds
      ),
    by = c("round", "team_abbrev")
  ) %>%
  transmute(
    run_ts = run_ts,
    team_abbrev,
    round,
    points_scored,
    points_conceded,
    tries_scored = NA_real_,
    tries_conceded = NA_real_,
    linebreaks_for = NA_real_,
    linebreaks_against = NA_real_,
    possession_share = NA_real_,
    territory_indicators = case_when(
      bye_flag %in% TRUE ~ "bye",
      TRUE ~ paste(
        paste0("ladder_pos=", coalesce_chr(ladder_position)),
        paste0("ladder_points=", coalesce_chr(ladder_points)),
        paste0("points_diff=", coalesce_chr(points_difference)),
        paste0("streak=", coalesce_chr(streak)),
        paste0("form=", coalesce_chr(form)),
        paste0("home_record=", coalesce_chr(home_record)),
        paste0("away_record=", coalesce_chr(away_record)),
        paste0("day_record=", coalesce_chr(day_record)),
        paste0("night_record=", coalesce_chr(night_record)),
        paste0("players_used=", coalesce_chr(players_used)),
        paste0("premiership_odds=", coalesce_chr(premiership_odds)),
        sep = "; "
      )
    ),
    completion_rate = NA_real_,
    attacking_trend_last_3,
    attacking_trend_last_5,
    defensive_trend_last_3,
    defensive_trend_last_5,
    left_edge_vulnerability = NA_real_,
    right_edge_vulnerability = NA_real_,
    middle_defensive_weakness = NA_real_
  )

matchup_context <- team_results_by_round %>%
  select(
    round, team_abbrev,
    team_recent_form = recent_form_last_3,
    team_attacking_trend_last_3 = attacking_trend_last_3,
    team_defensive_trend_last_3 = defensive_trend_last_3
  )

fixture_matchup_table <- team_schedule %>%
  left_join(matchup_context, by = c("round", "team_abbrev")) %>%
  left_join(
    matchup_context %>%
      transmute(
        round,
        opponent_abbrev = team_abbrev,
        opponent_recent_form = team_recent_form,
        opponent_attacking_trend_last_3 = team_attacking_trend_last_3,
        opponent_defensive_trend_last_3 = team_defensive_trend_last_3
      ),
    by = c("round", "opponent_abbrev")
  ) %>%
  mutate(
    projected_team_scoring_environment = if_else(
      bye_flag %in% TRUE,
      NA_real_,
      rowMeans(cbind(team_attacking_trend_last_3, opponent_defensive_trend_last_3), na.rm = TRUE)
    ),
    projected_game_total = if_else(
      bye_flag %in% TRUE,
      NA_real_,
      rowMeans(
        cbind(
          team_attacking_trend_last_3 + opponent_defensive_trend_last_3,
          opponent_attacking_trend_last_3 + team_defensive_trend_last_3
        ),
        na.rm = TRUE
      )
    ),
    projected_team_scoring_environment = if_else(is.nan(projected_team_scoring_environment), NA_real_, projected_team_scoring_environment),
    projected_game_total = if_else(is.nan(projected_game_total), NA_real_, projected_game_total),
    matchup_rating_by_team = projected_team_scoring_environment,
    matchup_rating_by_player = projected_team_scoring_environment,
    team_style_indicator = case_when(
      bye_flag %in% TRUE ~ "bye",
      !is.na(team_attacking_trend_last_3) & team_attacking_trend_last_3 >= 24 ~ "attack_first",
      !is.na(team_defensive_trend_last_3) & team_defensive_trend_last_3 <= 16 ~ "defensive_grind",
      !is.na(team_attacking_trend_last_3) ~ "balanced",
      TRUE ~ NA_character_
    )
  ) %>%
  arrange(team_abbrev, round, kickoff_at_utc) %>%
  group_by(team_abbrev) %>%
  mutate(
    next_2_rounds_difficulty = lookahead_mean_non_na(matchup_rating_by_team, 2),
    next_3_rounds_difficulty = lookahead_mean_non_na(matchup_rating_by_team, 3),
    next_5_rounds_difficulty = lookahead_mean_non_na(matchup_rating_by_team, 5),
    schedule_swing_indicator = case_when(
      is.na(next_2_rounds_difficulty) | is.na(next_5_rounds_difficulty) ~ NA_character_,
      next_2_rounds_difficulty >= next_5_rounds_difficulty + 3 ~ "easier_short_term",
      next_2_rounds_difficulty <= next_5_rounds_difficulty - 3 ~ "harder_short_term",
      TRUE ~ "stable"
    )
  ) %>%
  ungroup() %>%
  transmute(
    run_ts = run_ts,
    round,
    team_abbrev,
    opponent = opponent_abbrev,
    venue,
    home_away,
    days_rest,
    travel_burden,
    short_turnaround_flag,
    opponent_recent_form,
    team_recent_form,
    projected_game_total,
    projected_team_scoring_environment,
    opponent_defensive_weakness_by_position = NA_character_,
    opponent_attacking_weakness_by_position = NA_character_,
    team_style_indicator,
    bye_flag,
    major_outs_opponent = NA_character_,
    major_outs_team = NA_character_,
    matchup_rating_by_player,
    matchup_rating_by_team,
    next_2_rounds_difficulty,
    next_3_rounds_difficulty,
    next_5_rounds_difficulty,
    schedule_swing_indicator
  )

cash_generation_model <- player_catalog %>%
  left_join(initialvalue_catalog, by = c("full_name" = "player_name", "team_abbrev", "name_norm")) %>%
  left_join(latest_price_rollups, by = "player_id") %>%
  transmute(
    run_ts = run_ts,
    player_id,
    full_name,
    team_abbrev,
    starting_price = current_price_external,
    current_price = coalesce(current_price_history, current_price_external),
    price_change_last_round,
    cumulative_cash_generation,
    projected_price_rise_next_round = projected_price_next - coalesce(current_price_history, current_price_external),
    projected_price_fall_next_round = if_else(projected_price_next < coalesce(current_price_history, current_price_external), projected_price_next - coalesce(current_price_history, current_price_external), 0),
    breakeven_trend = NA_real_,
    games_until_peak_cash_estimate = NA_real_,
    cash_cow_maturity_status = case_when(
      !is.na(projected_price_next) & projected_price_next > coalesce(current_price_history, current_price_external) ~ "rising",
      !is.na(projected_price_next) & projected_price_next <= coalesce(current_price_history, current_price_external) ~ "near_peak_or_peaked",
      TRUE ~ NA_character_
    ),
    player_classification = case_when(
      !is.na(current_price_external) & current_price_external <= 350000 ~ "cash_cow",
      !is.na(current_price_external) & current_price_external >= 700000 ~ "keeper",
      !is.na(current_price_external) ~ "stepping_stone",
      TRUE ~ NA_character_
    )
  )

squad_round_enriched <- team_players_latest %>%
  left_join(
    player_price_rollups %>%
      select(player_id, round, score, mins, price, avg_3, avg_5),
    by = c("player_id", "round")
  ) %>%
  left_join(
    team_lookup %>% select(user_team_id, team_name, coach_name, is_me),
    by = "user_team_id"
  ) %>%
  left_join(
    player_catalog %>%
      select(player_id, team_abbrev),
    by = "player_id"
  ) %>%
  left_join(
    master_player_round_latest %>%
      select(player_id, full_name, positions, locked_flag, status),
    by = "player_id"
  ) %>%
  left_join(
    fixture_matchup_table %>%
      select(round, team_abbrev, bye_flag, next_3_rounds_difficulty),
    by = c("round", "team_abbrev")
  ) %>%
  group_by(user_team_id, player_id) %>%
  mutate(
    acquisition_round = min(round, na.rm = TRUE),
    acquisition_price = price[match(acquisition_round, round)],
    profit_or_loss = price - acquisition_price
  ) %>%
  ungroup() %>%
  mutate(
    current_role_security = case_when(
      !is.na(mins) & mins >= 50 ~ "high",
      !is.na(mins) & mins >= 30 ~ "medium",
      !is.na(mins) ~ "low",
      TRUE ~ NA_character_
    ),
    keeper_status = case_when(
      !is.na(price) & price >= 700000 ~ "keeper",
      !is.na(price) ~ "non_keeper",
      TRUE ~ NA_character_
    ),
    sell_urgency = case_when(
      status %in% c("Out", "Suspended") ~ "high",
      TRUE ~ "normal"
    ),
    cover_value = case_when(
      str_detect(coalesce(positions, ""), "/") ~ "high",
      TRUE ~ "standard"
    ),
    captaincy_value = avg_3,
    bye_usefulness = if_else(bye_flag %in% TRUE, 0, next_3_rounds_difficulty),
    dpp_flexibility_usefulness = if_else(str_detect(coalesce(positions, ""), "/"), 1, 0),
    injury_suspension_risk = status,
    currently_locked = locked_flag,
    selected_this_week = !is.na(position_sort) & position_sort <= 17,
    field_bench_npr = case_when(
      !is.na(position_sort) & position_sort <= 13 ~ "field",
      !is.na(position_sort) & position_sort <= 17 ~ "bench",
      !is.na(position_sort) ~ "npr",
      TRUE ~ NA_character_
    ),
    projected_score_this_week = avg_3,
    projected_score_next_3_weeks = avg_5,
    projected_value_change_next_3_weeks = NA_real_
  ) %>%
  select(
    run_ts, user_team_id, team_name, coach_name, is_me, round, player_id, full_name,
    acquisition_round, acquisition_price, current_price = price, profit_or_loss,
    current_role_security, keeper_status, sell_urgency, cover_value, captaincy_value,
    bye_usefulness, dpp_flexibility_usefulness, injury_suspension_risk,
    currently_locked, selected_this_week, field_bench_npr, projected_score_this_week,
    projected_score_next_3_weeks, projected_value_change_next_3_weeks
  )

latest_team_round_stats <- team_round_stats_history %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup()

# This table tracks SuperCoach league opponents and inferred fantasy trades, not real NRL matchups.
opponent_behaviour_history <- team_players_latest %>%
  group_by(user_team_id, round) %>%
  summarise(
    squad_player_ids = list(sort(unique(player_id))),
    .groups = "drop"
  ) %>%
  left_join(
    inferred_changes %>%
      group_by(user_team_id, round) %>%
      summarise(
        detected_run_ts = max(to_run_ts, na.rm = TRUE),
        inferred_trade_events = n(),
        inferred_players_out = sum(players_out_n, na.rm = TRUE),
        inferred_players_in = sum(players_in_n, na.rm = TRUE),
        inferred_trade_pairs = list(bind_rows(inferred_trade_pairs)),
        .groups = "drop"
      ),
    by = c("user_team_id", "round")
  ) %>%
  left_join(
    actual_trade_history %>%
      group_by(user_team_id, round) %>%
      summarise(
    actual_trade_count = n(),
    actual_trades = list(tibble(
      buy_player_id = buy_player_id,
      sell_player_id = sell_player_id,
      trade_source = trade_source
    )),
    .groups = "drop"
  ),
    by = c("user_team_id", "round")
  ) %>%
  left_join(
    latest_team_round_stats %>%
      select(user_team_id, round, total_changes, trade_boosts_used),
    by = c("user_team_id", "round")
  ) %>%
  left_join(
    team_lookup %>% select(user_team_id, team_name, coach_name, is_me),
    by = "user_team_id"
  ) %>%
  mutate(
    behaviour_source = case_when(
      !map_lgl(actual_trades, is.null) ~ "actual_api_plus_snapshots",
      TRUE ~ "snapshot_inference_plus_team_stats"
    )
  )

league_ownership_movement <- player_catalog %>%
  transmute(
    run_ts = run_ts,
    player_id,
    full_name,
    ownership_percentage = NA_real_,
    ownership_movement = NA_real_
  )

captaincy_vc_table <- team_players_latest %>%
  group_by(user_team_id, round, player_id) %>%
  summarise(
    captain_flag = NA,
    vice_captain_flag = NA,
    captaincy_source = "unavailable_from_confirmed_sources",
    .groups = "drop"
  )

structure_health_table <- squad_round_enriched %>%
  group_by(user_team_id, team_name, coach_name, is_me, round) %>%
  summarise(
    players_in_squad = n_distinct(player_id),
    selected_players = sum(selected_this_week %in% TRUE, na.rm = TRUE),
    field_players = sum(field_bench_npr == "field", na.rm = TRUE),
    bench_players = sum(field_bench_npr == "bench", na.rm = TRUE),
    npr_players = sum(field_bench_npr == "npr", na.rm = TRUE),
    locked_players = sum(currently_locked %in% TRUE, na.rm = TRUE),
    dpp_players = sum(dpp_flexibility_usefulness > 0, na.rm = TRUE),
    avg_projected_score_this_week = if_else(
      all(is.na(projected_score_this_week)),
      NA_real_,
      mean(projected_score_this_week, na.rm = TRUE)
    ),
    .groups = "drop"
  )

scenario_refresh_table <- tibble(
  run_ts = run_ts,
  current_round = current_round,
  competition_status = competition_status,
  is_lockout = safe_lgl(settings$competition$is_lockout, FALSE),
  is_partial_lockout = safe_lgl(settings$competition$is_partial_lockout, FALSE),
  next_refresh_trigger = safe_chr(settings$competition$lockout_start),
  refresh_reason = "competition_lockout_window"
)

long_horizon_planning_table <- squad_round_enriched %>%
  filter(is_me %in% TRUE) %>%
  group_by(user_team_id, team_name, coach_name) %>%
  filter(round == max(round, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(user_team_id, team_name, coach_name) %>%
  summarise(
    run_ts = max(run_ts),
    current_round = max(round),
    current_squad_value = sum(current_price, na.rm = TRUE),
    projected_score_next_3_weeks = sum(projected_score_next_3_weeks, na.rm = TRUE),
    trades_remaining = game_rules_round_state$trades_remaining[[1]],
    boosts_remaining = game_rules_round_state$boosts_remaining[[1]],
    finals_round = game_rules_round_state$finals_round[[1]],
    next_bye_rounds = list(game_rules_round_state$bye_round_structure[[1]]),
    .groups = "drop"
  )
```

## 14. Build cash and team value by round

```{r}
starting_cap <- 11950000L

# Sum player prices to rebuild each squad's market value by round.
team_prices_by_round <- team_players_latest %>%
  distinct(user_team_id, round, player_id) %>%
  left_join(
    player_price_history_sc %>%
      select(player_id, round, price),
    by = c("player_id", "round")
  ) %>%
  group_by(user_team_id, round) %>%
  summarise(
    squad_size = n(),
    n_players_priced = sum(!is.na(price)),
    squad_value_calc = if_else(
      n_players_priced == squad_size,
      sum(price, na.rm = TRUE),
      NA_real_
    ),
    .groups = "drop"
  )

team_round_rosters <- team_players_latest %>%
  distinct(user_team_id, round, player_id)

min_round_available <- min(team_round_rosters$round, na.rm = TRUE)
max_round_available <- max(team_round_rosters$round, na.rm = TRUE)

# Identify players newly in a roster compared with the prior round.
team_ins <- team_round_rosters %>%
  filter(round > min_round_available) %>%
  anti_join(
    team_round_rosters %>%
      mutate(round = round + 1L),
    by = c("user_team_id", "round", "player_id")
  ) %>%
  rename(player_id_in = player_id)

# Identify players removed from a roster compared with the prior round.
team_outs <- team_round_rosters %>%
  filter(round < max_round_available) %>%
  mutate(round = round + 1L) %>%
  anti_join(
    team_round_rosters,
    by = c("user_team_id", "round", "player_id")
  ) %>%
  rename(player_id_out = player_id)

# Price trade events using the prior round's price point.
trade_events_priced <- team_ins %>%
  group_by(user_team_id, round) %>%
  mutate(trade_slot = row_number()) %>%
  ungroup() %>%
  full_join(
    team_outs %>%
      group_by(user_team_id, round) %>%
      mutate(trade_slot = row_number()) %>%
      ungroup(),
    by = c("user_team_id", "round", "trade_slot")
  ) %>%
  left_join(
    player_price_history_sc %>%
      transmute(
        player_id_in = player_id,
        round = round + 1L,
        buy_price = price
      ),
    by = c("player_id_in", "round")
  ) %>%
  left_join(
    player_price_history_sc %>%
      transmute(
        player_id_out = player_id,
        round = round + 1L,
        sell_price = price
      ),
    by = c("player_id_out", "round")
  ) %>%
  mutate(
    cash_delta = coalesce(sell_price, 0) - coalesce(buy_price, 0)
  )

trade_cash_by_round <- trade_events_priced %>%
  group_by(user_team_id, round) %>%
  summarise(
    trade_ins = sum(!is.na(player_id_in)),
    trade_outs = sum(!is.na(player_id_out)),
    total_buy_price = sum(coalesce(buy_price, 0), na.rm = TRUE),
    total_sell_price = sum(coalesce(sell_price, 0), na.rm = TRUE),
    cash_delta = sum(cash_delta, na.rm = TRUE),
    .groups = "drop"
  )

initial_cash_by_team <- team_prices_by_round %>%
  group_by(user_team_id) %>%
  slice_min(round, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  transmute(
    user_team_id,
    initial_squad_value_calc = squad_value_calc,
    initial_cash_calc = starting_cap - squad_value_calc
  )

cash_by_round <- team_prices_by_round %>%
  left_join(trade_cash_by_round, by = c("user_team_id", "round")) %>%
  left_join(initial_cash_by_team, by = "user_team_id") %>%
  arrange(user_team_id, round) %>%
  group_by(user_team_id) %>%
  mutate(
    trade_ins = coalesce(trade_ins, 0L),
    trade_outs = coalesce(trade_outs, 0L),
    total_buy_price = coalesce(total_buy_price, 0),
    total_sell_price = coalesce(total_sell_price, 0),
    cash_delta = coalesce(cash_delta, 0),
    cash_end_round_calc = initial_cash_calc + cumsum(cash_delta),
    team_value_total_calc = squad_value_calc + cash_end_round_calc
  ) %>%
  ungroup()

negative_cash_check <- cash_by_round %>%
  filter(cash_end_round_calc < 0)

if (nrow(negative_cash_check) > 0) {
  print_results(negative_cash_check)
  stop("Stopping: negative cash balances remain after applying previous-round trade pricing")
}
```

## 15. Attach value fields back to ladder history safely and save outputs

```{r}
ladder_value_compare <- ladder_history %>%
  group_by(user_team_id, round) %>%
  slice_max(run_ts, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(user_team_id, round, squad_value) %>%
  left_join(
    cash_by_round %>%
      select(
        user_team_id,
        round,
        squad_size,
        n_players_priced,
        squad_value_calc,
        initial_cash_calc,
        trade_ins,
        trade_outs,
        total_buy_price,
        total_sell_price,
        cash_delta,
        cash_end_round_calc,
        team_value_total_calc
      ),
    by = c("user_team_id", "round")
  ) %>%
  mutate(
    squad_value_diff = squad_value_calc - squad_value
  )

ladder_history <- ladder_history %>%
  select(
    -any_of(c(
      "squad_size",
      "n_players_priced",
      "squad_value_calc",
      "initial_cash_calc",
      "trade_ins",
      "trade_outs",
      "total_buy_price",
      "total_sell_price",
      "cash_delta",
      "cash_end_round_calc",
      "team_value_total_calc",
      "squad_value_diff"
    ))
  ) %>%
  left_join(
    ladder_value_compare %>%
      select(
        user_team_id,
        round,
        squad_size,
        n_players_priced,
        squad_value_calc,
        initial_cash_calc,
        trade_ins,
        trade_outs,
        total_buy_price,
        total_sell_price,
        cash_delta,
        cash_end_round_calc,
        team_value_total_calc,
        squad_value_diff
      ),
    by = c("user_team_id", "round")
  )

checklist_coverage_status <- tibble(
  checklist_item = c(
    "game_rules_round_state",
    "master_player_table",
    "player_scoring_component_history",
    "team_list_role_certainty",
    "fixture_matchup_table",
    "team_performance_context",
    "cash_generation_model",
    "your_squad_table",
    "opponent_behaviour_history",
    "league_ownership_movement",
    "availability_risk_table",
    "captaincy_vc_table",
    "trade_candidate_comparison_table",
    "structure_health_table",
    "scenario_table",
    "long_horizon_planning_table"
  ),
  table_name = c(
    "game_rules_round_state",
    "master_player_round_latest",
    "player_scoring_component_history",
    "team_list_role_certainty",
    "fixture_matchup_table",
    "team_performance_context",
    "cash_generation_model",
    "squad_round_enriched",
    "opponent_behaviour_history",
    "league_ownership_movement",
    "availability_risk_table",
    "captaincy_vc_table",
    "trade_candidate_comparison_table",
    "structure_health_table",
    "scenario_refresh_table",
    "long_horizon_planning_table"
  ),
  row_count = c(
    nrow(game_rules_round_state),
    nrow(master_player_round_latest),
    nrow(player_scoring_component_history),
    nrow(team_list_role_certainty),
    nrow(fixture_matchup_table),
    nrow(team_performance_context),
    nrow(cash_generation_model),
    nrow(squad_round_enriched),
    nrow(opponent_behaviour_history),
    nrow(league_ownership_movement),
    nrow(availability_risk_table),
    nrow(captaincy_vc_table),
    0L,
    nrow(structure_health_table),
    nrow(scenario_refresh_table),
    nrow(long_horizon_planning_table)
  ),
  status = c(
    "partial",
    "partial",
    "partial",
    "partial",
    "partial",
    "partial",
    "partial",
    "partial",
    "partial",
    "unavailable",
    "partial",
    "unavailable",
    "unavailable",
    "partial",
    "partial",
    "partial"
  ),
  source_endpoint = c(
    "/settings, /players-cf, /userteams/{id}/statsPlayers",
    "/players-cf, initialvalue.php, data-yearplot.php",
    "data-yearplot.php",
    "/userteams/{id}/statsPlayers, data-yearplot.php",
    "https://www.nrl.com/draw/?round={round}, https://www.nrl.com/ladder/?round={round}",
    "https://www.nrl.com/draw/?round={round}, https://www.nrl.com/ladder/?round={round}",
    "initialvalue.php, data-yearplot.php",
    "/userteams/{id}/statsPlayers, /players-cf, data-yearplot.php",
    "/userteams/{id}/statsPlayers, ladderAndFixtures",
    "Unavailable from confirmed sources",
    "/players-cf",
    "Unavailable from confirmed sources",
    "Unavailable from confirmed sources",
    "/userteams/{id}/statsPlayers, /players-cf",
    "/settings",
    "/settings, /userteams/{id}/statsPlayers"
  ),
  notes = c(
    "Confirmed competition rules, lockout window, squad limits, bye rounds, and player lock state via list columns; Origin-specific rounds remain unavailable.",
    "Current price, status, team, DPP, history lists, and recent averages are confirmed; breakeven, ownership, role, goal-kicking, and return timeline remain unavailable.",
    "Confirmed score, minutes, price-derived volatility, floor, ceiling, and PPM; base-stat components are unavailable from confirmed sources.",
    "Confirmed squad selection order and recent minutes for league rosters; global NRL team lists, role threats, and late omission probabilities remain unavailable.",
    "Confirmed official NRL fixture, venue, bye, kickoff timing, home/away, days-rest, travel heuristic, and rolling matchup difficulty via draw and ladder pages; position-specific weakness and confirmed major outs remain unavailable.",
    "Confirmed official NRL scores, ladder position, streak, form, points differential, and rolling attacking/defensive trends via draw and ladder pages; tries, linebreaks, possession, and edge-split stats remain unavailable.",
    "Confirmed starting/current price, recent price movement, projected next price, and cash classification; breakeven trend and peak-cash timing remain unavailable.",
    "Confirmed acquisition timing, prices, lock state, selection slot, and simple projections; next-3-week value movement and bye utility remain approximate or unavailable.",
    "Confirmed full squad history, cumulative change counts, and boost usage by team-round; exact opponent ins/outs are only inferred from snapshots unless exposed for the authenticated team.",
    "Ownership percentage and movement were not present in the confirmed source set.",
    "Confirmed current active, injury/suspension, and lock indicators from /players-cf; expected return dates remain unavailable.",
    "Captain and vice-captain selections were not present in the confirmed source set.",
    "Trade comparison scenarios are not available from confirmed sources and were not fabricated.",
    "Confirmed structural metrics from squad composition and lock state; fixture-linked bye and schedule context are now available for downstream joins.",
    "Confirmed competition refresh trigger from /settings lockout window; official NRL draw now supplies per-round matchup refresh context.",
    "Confirmed long-horizon summary uses current squad value, trades, boosts, and bye rounds; deeper future projection fields remain partial."
  )
)

saveRDS(ladder_history, path_ladder_history)
saveRDS(fixture_triggers, path_fixture_triggers)
saveRDS(master_player_round_latest, path_master_player_round_latest)
saveRDS(opponent_behaviour_history, path_opponent_behaviour_history)
saveRDS(squad_round_enriched, path_squad_round_enriched)
saveRDS(game_rules_round_state, path_game_rules_round_state)
saveRDS(player_scoring_component_history, path_player_scoring_component_history)
saveRDS(team_list_role_certainty, path_team_list_role_certainty)
saveRDS(fixture_matchup_table, path_fixture_matchup_table)
saveRDS(team_performance_context, path_team_performance_context)
saveRDS(cash_generation_model, path_cash_generation_model)
saveRDS(league_ownership_movement, path_league_ownership_movement)
saveRDS(availability_risk_table, path_availability_risk_table)
saveRDS(captaincy_vc_table, path_captaincy_vc_table)
saveRDS(structure_health_table, path_structure_health_table)
saveRDS(scenario_refresh_table, path_scenario_refresh_table)
saveRDS(long_horizon_planning_table, path_long_horizon_planning_table)
saveRDS(checklist_coverage_status, path_checklist_coverage_status)
```

## 16. Validation summary

```{r}
major_tables <- list(
  game_rules_round_state = game_rules_round_state,
  master_player_round_latest = master_player_round_latest,
  player_scoring_component_history = player_scoring_component_history,
  team_list_role_certainty = team_list_role_certainty,
  fixture_matchup_table = fixture_matchup_table,
  team_performance_context = team_performance_context,
  cash_generation_model = cash_generation_model,
  squad_round_enriched = squad_round_enriched,
  opponent_behaviour_history = opponent_behaviour_history,
  availability_risk_table = availability_risk_table,
  structure_health_table = structure_health_table,
  long_horizon_planning_table = long_horizon_planning_table
)

row_count_summary <- tibble(
  table_name = names(major_tables),
  row_count = map_int(major_tables, nrow)
)

unresolved_gaps <- checklist_coverage_status %>%
  filter(status != "implemented")

sample_rows <- purrr::imap(
  major_tables,
  ~ if (nrow(.x) == 0) NULL else utils::head(.x, 1)
)

row_count_summary
unresolved_gaps %>% select(checklist_item, status, notes)
sample_rows
```

## 17. Final returned objects

```{r}
list(
  current_round = current_round,
  rounds_pulled = rounds_to_pull,
  ladder_history = ladder_history,
  fixtures_history = fixtures_history,
  competition_state_history = competition_state_history,
  players_cf_history = players_cf_history,
  players_cf_latest = players_cf_latest,
  player_history_refresh_log = player_history_refresh_log,
  source_refresh_log = source_refresh_log,
  team_players_latest = team_players_latest,
  team_round_stats_history = team_round_stats_history,
  actual_trade_history = actual_trade_history,
  inferred_changes = inferred_changes,
  grog_baguettes_latest = grog_baguettes_latest,
  grog_baguettes_changes = grog_baguettes_changes,
  league_change_summary = league_change_summary,
  run_log = run_log,
  team_round_results = team_round_results,
  player_price_history_sc = player_price_history_sc,
  master_player_round_latest = master_player_round_latest,
  player_scoring_component_history = player_scoring_component_history,
  team_list_role_certainty = team_list_role_certainty,
  cash_generation_model = cash_generation_model,
  squad_round_enriched = squad_round_enriched,
  opponent_behaviour_history = opponent_behaviour_history,
  cash_by_round = cash_by_round,
  ladder_value_compare = ladder_value_compare,
  fixture_triggers = fixture_triggers,
  game_rules_round_state = game_rules_round_state,
  fixture_matchup_table = fixture_matchup_table,
  team_performance_context = team_performance_context,
  availability_risk_table = availability_risk_table,
  structure_health_table = structure_health_table,
  scenario_refresh_table = scenario_refresh_table,
  long_horizon_planning_table = long_horizon_planning_table,
  checklist_coverage_status = checklist_coverage_status
)
```
